---
title: "FSL Data quality and plausibility Report"
subtitle: "`r Sys.Date()`"
output: html_document
params:
  mainData: NULL
  uuidVar: "uuid"
  YesNoTeam: "no"
  TeamVar: "team"
  GroupVar: "enum_id"
---

<style>
.tocify-subheader {
  font-size: 0.7em;
}
.tocify-item {
  font-size: 0.85em;
  padding-left: 25px;
  text-indent: 0;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
options(scipen = 999)
```

```{r, include=FALSE, eval=TRUE}

raw.main <- params$mainData

```

# {.tabset .tabset-fade}

## Introduction

```{r, results='asis'}
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What is this tool?"))
  cat('\nThe FSL Data Quality and Plausibility Report serves as a crucial tool for assessing the reliability and accuracy of the data collection of FSL indicators across different assessments. This comprehensive analysis is designed to identify and address potential issues within the data, ensuring that field teams are being informed on potential issues detected in the data collection.\n\nThe report provides a detailed examination of the datasets, employing a variety of metrics and methodologies to evaluate data quality and plausibility. This includes checks for completeness, consistency, and accuracy of the data collected. This report aims to uncover any discrepancies, outliers, or anomalies that may suggest data collection, entry errors, or underlying issues that could impact the integrity of the findings.</p>')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What is in this tool?")) 
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "FSL SECTION"))
  cat('\nThis section includes:\n\n- Overall Plausibility Report / By Enumerator\n- All the flags related to Food Security and Livelihoods (details shown for each flag in the section)\n- Plots showing the distribution of the data.')

  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What to do next?"))
  cat('\nPlease check each flag and the <strong>ACTION</strong> related to it and act accordingly.\n\nAnother output will be associated to this HTML, the Excel file of the flags that were fired and requires follow-up with the field team. Please check the README tab in the excel file. This file will again be generated with the full data during the cleaning of the dataset. So please do use this file during data collection and relate to it in the final one to be filled.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "Feedback"))
  cat('\nFeedback on improvements to this product can be done through reaching out to:\n\n-abraham.azar@impact-initiatives.org \n\n-impact.geneva.phu@impact-initiatives.org')
```

## FSL {.tabset .tabset-fade}

```{r, echo=FALSE, warning=FALSE,include=FALSE}

  uuid_main <- params$uuidVar

  ## Set Team column

    yes_no_team <- params$YesNoTeam
 
    team <- params$TeamVar
  
  ## Set Enumerator column
  enumerator <- params$GroupVar
  
      fcs_check_columns <- c("fsl_fcs_cereal",
                           "fsl_fcs_legumes",
                           "fsl_fcs_veg",
                           "fsl_fcs_fruit",
                           "fsl_fcs_meat",
                           "fsl_fcs_dairy",
                           "fsl_fcs_sugar",
                           "fsl_fcs_oil")
      
      rcsi_check_columns <- c("fsl_rcsi_lessquality",
                            "fsl_rcsi_borrow",
                            "fsl_rcsi_mealsize",
                            "fsl_rcsi_mealadult",
                            "fsl_rcsi_mealnb")

      hhs_check_columns <- c("fsl_hhs_nofoodhh",
                           "fsl_hhs_sleephungry",
                           "fsl_hhs_alldaynight")
    
    hhs_check_columns_freq <- c("fsl_hhs_nofoodhh_freq",
                                "fsl_hhs_sleephungry_freq",
                                "fsl_hhs_alldaynight_freq")
      
## FCS
raw.flag.fcs <- raw.main %>%
  check_fsl_flags2(
    # fsl_fcs_cereal = fsl_fcs_cereal,
    #                            fsl_fcs_legumes = fsl_fcs_legumes,
    #                            fsl_fcs_veg = fsl_fcs_veg,
    #                            fsl_fcs_fruit = fsl_fcs_fruit,
    #                            fsl_fcs_meat = fsl_fcs_meat,
    #                            fsl_fcs_dairy = fsl_fcs_dairy,
    #                            fsl_fcs_sugar = fsl_fcs_sugar,
    #                            fsl_fcs_oil = fsl_fcs_oil,
    #                            fsl_lcsi_stress1 = fsl_lcsi_stress1,
    #                            fsl_lcsi_stress2 = fsl_lcsi_stress2,
    #                            fsl_lcsi_stress3 = fsl_lcsi_stress3,
    #                            fsl_lcsi_stress4 = fsl_lcsi_stress4,
    #                            fsl_lcsi_crisis1 = fsl_lcsi_crisis1,
    #                            fsl_lcsi_crisis2 = fsl_lcsi_crisis2,
    #                            fsl_lcsi_crisis3 = fsl_lcsi_crisis3,
    #                            fsl_lcsi_emergency1 = fsl_lcsi_emergency1,
    #                            fsl_lcsi_emergency2 = fsl_lcsi_emergency2,
    #                            fsl_lcsi_emergency3 = fsl_lcsi_emergency3,
    #                            fsl_hhs_nofoodhh = fsl_hhs_nofoodhh,
    #                            fsl_hhs_nofoodhh_freq = fsl_hhs_nofoodhh_freq,
    #                            fsl_hhs_sleephungry = fsl_hhs_sleephungry,
    #                            fsl_hhs_sleephungry_freq = fsl_hhs_sleephungry_freq,
    #                            fsl_hhs_alldaynight = fsl_hhs_alldaynight,
    #                            fsl_hhs_alldaynight_freq = fsl_hhs_alldaynight_freq,
    #                            fsl_rcsi_lessquality = fsl_rcsi_lessquality,
    #                            fsl_rcsi_borrow = fsl_rcsi_borrow,
    #                            fsl_rcsi_mealsize = fsl_rcsi_mealsize,
    #                            fsl_rcsi_mealadult = fsl_rcsi_mealadult,
    #                            fsl_rcsi_mealnb = fsl_rcsi_mealnb,
    #                            fsl_hdds_cereals = fsl_hdds_cereals, 
    #                            fsl_hdds_tubers = fsl_hdds_tubers,
    #                            fsl_hdds_legumes = fsl_hdds_legumes, 
    #                            fsl_hdds_veg = fsl_hdds_veg,
    #                            fsl_hdds_fruit = fsl_hdds_fruit, 
    #                            fsl_hdds_meat = fsl_hdds_meat,
    #                            fsl_hdds_fish = fsl_hdds_fish, 
    #                            fsl_hdds_dairy = fsl_hdds_dairy,
    #                            fsl_hdds_eggs = fsl_hdds_eggs, 
    #                            fsl_hdds_sugar = fsl_hdds_sugar,
    #                            fsl_hdds_oil = fsl_hdds_oil, 
    #                            fsl_hdds_condiments = fsl_hdds_condiments,
                               uuid = uuid_main
                   )

list_of_var <- c("uuid_main","FSL_indicators","num_children","income_types", "fsl_fcs_cereal","fsl_fcs_legumes",
                 "fsl_fcs_veg","fsl_fcs_fruit","fsl_fcs_meat","fsl_fcs_dairy","fsl_fcs_sugar",
                 "fsl_fcs_oil","fsl_rcsi_lessquality","fsl_rcsi_borrow","fsl_rcsi_mealsize","fsl_rcsi_mealadult",
                 "fsl_rcsi_mealnb","fsl_hhs_nofoodhh","fsl_hhs_nofoodhh_freq","fsl_hhs_sleephungry","fsl_hhs_sleephungry_freq",
                 "fsl_hhs_alldaynight","fsl_hhs_alldaynight_freq","yes_answer","no_answer","rarely_answer","sometimes_answer","often_answer",
                 "fsl_lcsi_stress1","fsl_lcsi_stress2","fsl_lcsi_stress3","fsl_lcsi_stress4","yes_val_hdds","no_val_hdds",
                 "fsl_lcsi_crisis1","fsl_lcsi_crisis2","fsl_lcsi_crisis3","fsl_lcsi_emergency1",
                 "fsl_lcsi_emergency2","fsl_lcsi_emergency3","yes_val","no_val","exhausted_val","not_applicable_val",
                 "fsl_hdds_cereals","fsl_hdds_tubers","fsl_hdds_veg","fsl_hdds_fruit","fsl_hdds_meat",
                 "fsl_hdds_eggs","fsl_hdds_fish","fsl_hdds_legumes","fsl_hdds_dairy","fsl_hdds_oil","fsl_hdds_sugar","fsl_hdds_condiments",
                 "fclcm_check_columns","fcm_check_1_columns","fcm_check_2_columns","fcm_check_3_columns",
                 "fcm_check_4_columns","fcm_check_5_columns","fcm_check_6_columns","hhs_check_columns_freq",
                 "residency_status","value_idp","team","yes_no_team",
                 "hdds_check_columns","lcsi_check_columns","hhs_check_columns","rcsi_check_columns","fcs_check_columns", "enumerator")

# if(!file.exists("inputs/environment.Rdata")){
#   save(list = list_of_var, file = "inputs/environment.Rdata")
# }
```

```{r, include = FALSE}
## Read the Plausibility excel file
overall_fsl_plaus <- openxlsx::read.xlsx(xlsxFile = "overall_plaus.xlsx", fillMergedCells = TRUE, sheet = "FSL") %>%
  dplyr::distinct()

result <- impactR4PHU::create_fsl_plaus(raw.flag.fcs,
                                        # fsl_fcs_cereal = fsl_fcs_cereal,
                                        # fsl_fcs_legumes = fsl_fcs_legumes,
                                        # fsl_fcs_dairy = fsl_fcs_dairy,
                                        # fsl_fcs_meat = fsl_fcs_meat, 
                                        # fsl_fcs_veg = fsl_fcs_veg,
                                        # fsl_fcs_fruit = fsl_fcs_fruit, 
                                        # fsl_fcs_oil = fsl_fcs_oil,
                                        # fsl_fcs_sugar = fsl_fcs_sugar, 
                                        # fsl_rcsi_lessquality = fsl_rcsi_lessquality,
                                        # fsl_rcsi_borrow = fsl_rcsi_borrow, 
                                        # fsl_rcsi_mealsize = fsl_rcsi_mealsize,
                                        # fsl_rcsi_mealadult = fsl_rcsi_mealadult, 
                                        # fsl_rcsi_mealnb = fsl_rcsi_mealnb,
                                        uuid = uuid_main)

result_fsl_enum <- impactR4PHU::create_fsl_plaus(raw.flag.fcs,
                                        # fsl_fcs_cereal = "fsl_fcs_cereal",
                                        # fsl_fcs_legumes = "fsl_fcs_legumes",
                                        # fsl_fcs_dairy = "fsl_fcs_dairy",
                                        # fsl_fcs_meat = "fsl_fcs_meat", 
                                        # fsl_fcs_veg = "fsl_fcs_veg",
                                        # fsl_fcs_fruit = "fsl_fcs_fruit", 
                                        # fsl_fcs_oil = "fsl_fcs_oil",
                                        # fsl_fcs_sugar = "fsl_fcs_sugar", 
                                        # fsl_rcsi_lessquality = "fsl_rcsi_lessquality",
                                        # fsl_rcsi_borrow = "fsl_rcsi_borrow", 
                                        # fsl_rcsi_mealsize = "fsl_rcsi_mealsize",
                                        # fsl_rcsi_mealadult = "fsl_rcsi_mealadult", 
                                        # fsl_rcsi_mealnb = "fsl_rcsi_mealnb",
                                        uuid = uuid_main,
                                        grouping = enumerator)
result_pivot <- result %>%
  dplyr::mutate_all(., as.character) %>%
  tidyr::pivot_longer(cols = everything(),names_to = "Criteria",
               values_to = "Score") %>%
  filter(stringr::str_starts(Criteria,"plaus_"))

bind <- data.frame(`Indicator Score` = c("plaus_fcs","plaus_fcs","plaus_fcs","plaus_fcs","plaus_fcs","plaus_fcs",
                                         "plaus_fcs","plaus_fcs","plaus_fcs","plaus_fcs","plaus_fcs","plaus_fcs",
                                         "plaus_rcsi","plaus_rcsi","plaus_rcsi","plaus_rcsi","plaus_rcsi",
                                         "plaus_rcsi","plaus_rcsi","plaus_rcsi","plaus_rcsi","plaus_rcsi",
                                         "plaus_hhs","plaus_hhs",
                                         "plaus_lcsi","plaus_lcsi","plaus_lcsi","plaus_lcsi","plaus_lcsi",
                                         "plaus_lcsi","plaus_lcsi","plaus_lcsi","plaus_lcsi","plaus_lcsi",
                                         "plaus_other_fsl","plaus_other_fsl","plaus_other_fsl",
                                         "plaus_other_fsl","plaus_other_fsl","plaus_other_fsl",
                                         "plaus_other_fsl","plaus_other_fsl","plaus_other_fsl",
                                         "plaus_other_fsl","plaus_other_fsl","plaus_other_fsl",NA,NA))

overall_fsl_plaus_overall <- overall_fsl_plaus%>%
  dplyr::left_join(result_pivot, by = c("flag_name"="Criteria")) %>%
  dplyr::mutate_all(., ~ifelse(is.na(.),"NA",.)) %>%
  cbind(bind)%>%
  dplyr::left_join(result_pivot %>% filter(Criteria %in% c("plaus_other_fsl",
                                                    "plaus_lcsi",
                                                    "plaus_hhs",
                                                    "plaus_rcsi",
                                                    "plaus_fcs")) %>%
              rename(indscore = "Score"), by = c("Indicator.Score"="Criteria")) %>%
  dplyr::mutate(indscore = case_when(flag_name == "plaus_flag_severe_hhs"~paste0(indscore,"/10"),
                              TRUE ~paste0(indscore,"/20"))) %>%
  dplyr::select(-Indicator.Score)

fsl <- flextable::flextable(overall_fsl_plaus_overall)


final_table <- impactR4PHU::create_plaus_table_fsl(fsl)

```

### Data Quality FSL {.tabset .tabset-fade}

#### Plausibility {.tabset .tabset-fade}

##### Overall

```{r}
final_table
```

```{r, results='asis'}
result_fsl_pivot <- result_fsl_enum %>%
  dplyr::mutate_all(., as.character) %>%
  tidyr::pivot_longer(-group,names_to = "Criteria",
               values_to = "Score") %>%
  filter(stringr::str_starts(Criteria,"plaus_"))
if(yes_no_team == "yes"){
  list_teams <- raw.main[[team]] %>% unique()
  list_teams <- list_teams[!is.na(list_teams)]
  for (i in list_teams) {
    cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong> {.tabset .tabset-fade}"))
    list_enum <- raw.main %>% 
      dplyr::filter(!!rlang::sym(team) == i) %>% 
      dplyr::pull(!!rlang::sym(enumerator)) %>% 
      unique()
    for(j in list_enum){
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",6), collapse=""), " ", "<strong>",j,"</strong>"))
      overall_fsl_plaus_enum <- overall_fsl_plaus %>%
        dplyr::left_join(result_fsl_pivot %>% filter(group == j), by = c("flag_name"="Criteria"))%>%
        dplyr::mutate_all(., ~ifelse(is.na(.),"NA",.)) %>%
        cbind(bind) %>%
        dplyr::select(-group) %>%
        dplyr::left_join(result_fsl_pivot %>%
                    filter(group == j) %>%
                    filter(Criteria %in% c("plaus_other_fsl",
                                           "plaus_lcsi",
                                           "plaus_hhs",
                                           "plaus_rcsi",
                                           "plaus_fcs")) %>%
                  dplyr::rename(indscore = "Score"), by = c("Indicator.Score"="Criteria")) %>%
        dplyr::mutate(indscore = dplyr::case_when(flag_name == "plaus_flag_severe_hhs"~paste0(indscore,"/10"),
                                  TRUE ~paste0(indscore,"/20"))) %>%
        dplyr::select(-c(Indicator.Score,group))
    
      fsl_enum <- flextable::flextable(overall_fsl_plaus_enum)
    
      final_table_fsl_enum <- impactR4PHU::create_plaus_table_fsl(fsl_enum)
      subch(final_table_fsl_enum)
    }
  }
} else {
  list_enum <- result_fsl_pivot$group %>% unique
  for (i in list_enum) {
    cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong>"))
    overall_fsl_plaus_enum <- overall_fsl_plaus %>%
      dplyr::left_join(result_fsl_pivot %>% filter(group == i), by = c("flag_name"="Criteria"))%>%
      dplyr::mutate_all(., ~ifelse(is.na(.),"NA",.)) %>%
      cbind(bind) %>%
      dplyr::select(-group) %>%
      dplyr::left_join(result_fsl_pivot %>%
                  filter(group == i) %>%
                  filter(Criteria %in% c("plaus_other_fsl",
                                         "plaus_lcsi",
                                         "plaus_hhs",
                                         "plaus_rcsi",
                                         "plaus_fcs")) %>%
                dplyr::rename(indscore = "Score"), by = c("Indicator.Score"="Criteria")) %>%
      dplyr::mutate(indscore = dplyr::case_when(flag_name == "plaus_flag_severe_hhs"~paste0(indscore,"/10"),
                                TRUE ~paste0(indscore,"/20"))) %>%
      dplyr::select(-c(Indicator.Score,group))
  
    fsl_enum <- flextable::flextable(overall_fsl_plaus_enum)
  
    final_table_fsl_enum <- impactR4PHU::create_plaus_table_fsl(fsl_enum)
    subch(final_table_fsl_enum)
  }
}
```


```{r, results='asis'}
flag_description <- readxl::read_excel("flag_description.xlsx", sheet = "FSL")
flags_fsl_columns <- names(raw.flag.fcs)[stringr::str_starts(names(raw.flag.fcs),"flag_")]
writexl::write_xlsx(as.data.frame(flags_fsl_columns), "test_flag_columnnames.xlsx")
overall_flag <- tibble()
for(i in 1:length(flags_fsl_columns)) {
  
  flag <- flags_fsl_columns[[i]]
  
  flag_overall <- raw.flag.fcs %>%
    dplyr::select(enumerator, !!rlang::sym(flag)) %>%
    filter(!is.na(!!rlang::sym(flag))) %>%
    dplyr::mutate(flag := flag) %>%
    dplyr::group_by(flag) %>%
    dplyr::summarise(num_samples = n(),
              flagged = sum(!!rlang::sym(flag))) %>%
    dplyr::mutate(percentage_flaggged = paste0(round((flagged/num_samples)*100,2),"%")) %>%
    dplyr::ungroup()
  if(nrow(flag_overall)>0){
    overall_flag <- rbind(overall_flag,flag_overall)
  }
}

writexl::write_xlsx(as.data.frame(overall_flag), "testing_overall_flag.xlsx")

add_to_html.title("Overall Flag Table")
subch(DT::datatable(overall_flag,
                  extensions = 'Buttons', options = list(
                    dom = 'Blfrtip',
                    buttons = c('copy', 'csv', 'excel', 'pdf'),
                    lengthMenu = list(c(50),
                                      c('All')),
                    paging = T)))

for(i in 1:length(flags_fsl_columns)) {
  
  flag <- flags_fsl_columns[[i]]
  
  writexl::write_xlsx(as.data.frame(flag), "testing_flag_name.xlsx")

  flag_rational <- flag_description %>%
    filter(flag_name %in% flag) %>%
    dplyr::pull(Rationale)
  flag_action <- flag_description %>%
    filter(flag_name %in% flag) %>%
    dplyr::pull(Action)
  flag_by_enum <- raw.flag.fcs %>%
    dplyr::select(enumerator, !!rlang::sym(flag)) %>%
    filter(!is.na(!!rlang::sym(flag))) %>%
    dplyr::mutate(flag := flag) %>%
    dplyr::group_by(flag,!!rlang::sym(enumerator)) %>%
    dplyr::summarise(num_samples = n(),
              flagged = sum(!!rlang::sym(flag))) %>%
    dplyr::mutate(percentage_flagged = paste0(round((flagged/num_samples)*100,2),"%")) %>%
    dplyr::ungroup() %>%
    dplyr::select(-1)
  if(nrow(flag_by_enum)>0){
    add_to_html.title(flag)
    cat("\n")
    cat(paste("<em><strong>Rational</strong>: ",flag_rational,"</em>\n"))
    if(!is.null(flag_action)){
      cat("\n")
      cat(paste("<em><strong>Action</strong>: ",flag_action,"</em>\n"))
    }
    subch(DT::datatable(flag_by_enum,
                  extensions = 'Buttons', options = list(
                    dom = 'Blfrtip',
                    buttons = c('copy', 'csv', 'excel', 'pdf'),
                    lengthMenu = list(c(50),
                                      c('All')),
                    paging = T)))
  }
}

writexl::write_xlsx(as.data.frame(flag_by_enum), "testing_flag_by_enum.xlsx")

```

### Plots {.tabset .tabset-fade}

#### FCS Ridge Overall Distribution Plot

```{r, results='asis'}
if(all(fcs_check_columns %in% names(raw.flag.fcs))) {
  impactR4PHU::plot_ridge_distribution(raw.flag.fcs, numeric_cols = c("fsl_fcs_cereal", "fsl_fcs_dairy", "fsl_fcs_veg", 
                                                                       "fsl_fcs_fruit", "fsl_fcs_legumes", "fsl_fcs_sugar", 
                                                                       "fsl_fcs_oil","fsl_fcs_meat"),
                                        name_groups = "Food Groups", name_units = "Days")
} else {
  cat("No Plot Produced!!")
}
```

#### FCS Ridge by Team/Enumerator Distribution Plot {.tabset .tabset-fade}

```{r, results='asis'}
if(all(fcs_check_columns %in% names(raw.flag.fcs))) {
  if(yes_no_team == "yes"){
    for (i in list_teams) {
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong>"))
      list_enum <- raw.main %>% 
        dplyr::filter(!!rlang::sym(team) == i) %>% 
        dplyr::pull(!!rlang::sym(enumerator))%>% 
        unique()
      
      subch(impactR4PHU::plot_ridge_distribution(raw.flag.fcs %>% 
                                              dplyr::filter(!!rlang::sym(enumerator) %in% list_enum), numeric_cols = c("fsl_fcs_cereal", "fsl_fcs_dairy", "fsl_fcs_veg", 
                                                                       "fsl_fcs_fruit", "fsl_fcs_legumes", "fsl_fcs_sugar", 
                                                                       "fsl_fcs_oil","fsl_fcs_meat"),
                                            name_groups = "Food Groups", name_units = "Days", 
                                            grouping = enumerator),
            fig_height = 8, fig_width = 10)
    }
  } else {
    (impactR4PHU::plot_ridge_distribution(raw.flag.fcs, numeric_cols = c("fsl_fcs_cereal", "fsl_fcs_dairy", "fsl_fcs_veg", 
                                                                       "fsl_fcs_fruit", "fsl_fcs_legumes", "fsl_fcs_sugar", 
                                                                       "fsl_fcs_oil","fsl_fcs_meat"),
                                          name_groups = "Food Groups", name_units = "Days", 
                                          grouping = enumerator))
  }
} else {
  cat("No Plot Produced!!")
}
```

#### RCSI Ridge Overall Distribution Plot

```{r, results='asis'}
if(all(rcsi_check_columns %in% names(raw.flag.fcs))) {
  (impactR4PHU::plot_ridge_distribution(raw.flag.fcs, numeric_cols = c("fsl_rcsi_lessquality", "fsl_rcsi_borrow",
                                                                       "fsl_rcsi_mealsize", "fsl_rcsi_mealadult", 
                                                                       "fsl_rcsi_mealnb"),
                                        name_groups = "Food Coping Strategy", name_units = "Days"))
} else {
  cat("No Plot Produced!!")
}
```

#### RCSI Ridge by Team/Enumerator Distribution Plot {.tabset .tabset-fade}

```{r, results='asis'}
if(all(rcsi_check_columns %in% names(raw.flag.fcs))) {
  if(yes_no_team == "yes"){
    for (i in list_teams) {
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong>"))
      list_enum <- raw.main %>% 
        dplyr::filter(!!rlang::sym(team) == i) %>% 
        dplyr::pull(!!rlang::sym(enumerator))%>% 
        unique()
      subch(impactR4PHU::plot_ridge_distribution(raw.flag.fcs %>% 
                                              dplyr::filter(!!rlang::sym(enumerator) %in% list_enum), numeric_cols = c("fsl_rcsi_lessquality", "fsl_rcsi_borrow",
                                                                       "fsl_rcsi_mealsize", "fsl_rcsi_mealadult", 
                                                                       "fsl_rcsi_mealnb"),
                                          name_groups = "Food Coping Strategy", name_units = "Days", 
                                          grouping = enumerator),
            fig_height = 8, fig_width = 10)
    }
  } else {
  (impactR4PHU::plot_ridge_distribution(raw.flag.fcs, numeric_cols = c("fsl_rcsi_lessquality", "fsl_rcsi_borrow",
                                                                       "fsl_rcsi_mealsize", "fsl_rcsi_mealadult", 
                                                                       "fsl_rcsi_mealnb"),
                                        name_groups = "Food Coping Strategy", name_units = "Days", 
                                        grouping = enumerator))
     }
  } else {
  cat("No Plot Produced!!")
}

```

#### FCS/RCSI/HHS Correlation Plot

```{r, results='asis'}

writexl::write_xlsx(raw.flag.fcs, "test_dataset_flags.xlsx")

if(all(fcs_check_columns %in% names(raw.flag.fcs)) &
   all(rcsi_check_columns %in% names(raw.flag.fcs)) &
   all(hhs_check_columns %in% names(raw.flag.fcs))) {
  (impactR4PHU::plot_correlogram(raw.flag.fcs, numeric_cols = c("fsl_fcs_score",  "fsl_rcsi_score",  "fsl_hhs_score")))
} else {
   cat("No Plot Produced!!")
}


```
