---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## impactR4PHU

<!-- badges: start -->
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](code_of_conduct.md)
[![R-CMD-check](https://github.com/impact-initiatives/impactR4PHU/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/impact-initiatives/impactR4PHU/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/impact-initiatives/impactR4PHU/graph/badge.svg?token=BG57ECHOYX)](https://codecov.io/gh/impact-initiatives/impactR4PHU)
<!-- badges: end -->



## Overview
`impactR4PHU` is designed for creating quality check reports, cleaning, analysing and outputing results of core outcome indicators of Public Health Unit. This package will target mainly Food Security and Livelihoods, WASH, Nutrition and Health Sectors. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` {r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("impact-initiatives/impactR4PHU")
```


## Adding indicators (for both Analysis or Quality checks)

```{r include=T,eval=T}
library(impactR4PHU)
df <- impactR4PHU_data_template
```

### Example:: Add Food Consumption Score (FCS)
``` {r eval=T,warning=F}
df_with_fcs <- df %>% add_fcs(
  cutoffs = "normal",
  fsl_fcs_cereal = "fsl_fcs_cereal",
  fsl_fcs_legumes = "fsl_fcs_legumes",
  fsl_fcs_veg = "fsl_fcs_veg",
  fsl_fcs_fruit = "fsl_fcs_fruit",
  fsl_fcs_meat = "fsl_fcs_meat",
  fsl_fcs_dairy = "fsl_fcs_dairy",
  fsl_fcs_sugar = "fsl_fcs_sugar",
  fsl_fcs_oil = "fsl_fcs_oil"
)
df_with_fcs %>%
  dplyr::select(
    uuid, fsl_fcs_score, fsl_fcs_cat, fcs_weight_cereal1, fcs_weight_legume2,
    fcs_weight_dairy3, fcs_weight_meat4, fcs_weight_veg5,
    fcs_weight_fruit6, fcs_weight_oil7, fcs_weight_sugar8
  ) %>%
  head(20)


```

### Example:: Add Household Hunger Scale (HHS)
``` {r, eval=TRUE, warning=F}
df_with_hhs <- df_with_fcs %>% add_hhs(
  fsl_hhs_nofoodhh = "fsl_hhs_nofoodhh",
  fsl_hhs_nofoodhh_freq = "fsl_hhs_nofoodhh_freq",
  fsl_hhs_sleephungry = "fsl_hhs_sleephungry",
  fsl_hhs_sleephungry_freq = "fsl_hhs_sleephungry_freq",
  fsl_hhs_alldaynight = "fsl_hhs_alldaynight",
  fsl_hhs_alldaynight_freq = "fsl_hhs_alldaynight_freq",
  yes_answer = "yes",
  no_answer = "no",
  rarely_answer = "rarely",
  sometimes_answer = "sometimes",
  often_answer = "often"
)
df_with_hhs %>%
  dplyr::select(
    uuid, fsl_hhs_comp1, fsl_hhs_comp2, fsl_hhs_comp3,
    fsl_hhs_score, fsl_hhs_cat_ipc, fsl_hhs_cat, num_hh
  ) %>%
  head(20)
```

### Example:: Add Livelihood Coping Strategy score (LCSI)
``` {r, eval=TRUE, warning=F}
df_with_lcsi <- df_with_hhs %>% add_lcsi(
  fsl_lcsi_stress1 = "fsl_lcsi_stress1",
  fsl_lcsi_stress2 = "fsl_lcsi_stress2",
  fsl_lcsi_stress3 = "fsl_lcsi_stress3",
  fsl_lcsi_stress4 = "fsl_lcsi_stress4",
  fsl_lcsi_crisis1 = "fsl_lcsi_crisis1",
  fsl_lcsi_crisis2 = "fsl_lcsi_crisis2",
  fsl_lcsi_crisis3 = "fsl_lcsi_crisis3",
  fsl_lcsi_emergency1 = "fsl_lcsi_emergency1",
  fsl_lcsi_emergency2 = "fsl_lcsi_emergency2",
  fsl_lcsi_emergency3 = "fsl_lcsi_emergency3",
  yes_val = "yes",
  no_val = "no_had_no_need",
  exhausted_val = "no_exhausted",
  not_applicable_val = "not_applicable"
)
df_with_lcsi %>%
  dplyr::select(uuid, fsl_lcsi_cat, fsl_lcsi_cat_exhaust, fsl_lcsi_cat_yes) %>%
  head(20)
```

### Example:: Add Reduced Household Coping Strategy score (rCSI)
``` {r, eval=TRUE, warning=F}
df_with_rcsi <- df_with_lcsi %>% add_rcsi(
  fsl_rcsi_lessquality = "fsl_rcsi_lessquality",
  fsl_rcsi_borrow = "fsl_rcsi_borrow",
  fsl_rcsi_mealsize = "fsl_rcsi_mealsize",
  fsl_rcsi_mealadult = "fsl_rcsi_mealadult",
  fsl_rcsi_mealnb = "fsl_rcsi_mealnb"
)
df_with_rcsi %>%
  dplyr::select(uuid, fsl_rcsi_score, fsl_rcsi_cat) %>%
  head(20)
```

### Example:: Add Household Dietary Diversity Score (HDDS)
``` {r, eval=TRUE, warning=F}
df_with_hdds <- df_with_rcsi %>% add_hdds(
   fsl_hdds_cereals = "fsl_hdds_cereals",
   fsl_hdds_tubers = "fsl_hdds_tubers",
   fsl_hdds_veg = "fsl_hdds_veg",
   fsl_hdds_fruit = "fsl_hdds_fruit",
   fsl_hdds_meat = "fsl_hdds_meat",
   fsl_hdds_eggs = "fsl_hdds_eggs",
   fsl_hdds_fish = "fsl_hdds_fish",
   fsl_hdds_legumes = "fsl_hdds_legumes",
   fsl_hdds_dairy = "fsl_hdds_dairy",
   fsl_hdds_oil = "fsl_hdds_oil",
   fsl_hdds_sugar = "fsl_hdds_sugar",
   fsl_hdds_condiments = "fsl_hdds_condiments"
)
df_with_hdds %>%
  dplyr::select(uuid, fsl_hdds_score, fsl_hdds_cat) %>%
  head(20)


```


### Example:: Add Food Consumption Matrix (FCM) using FCS, RCSI, and HHS
**Notice that these functions are also pipable**
``` {r, eval=TRUE, warning=F}
df_with_fcm_1 <- df_with_hdds %>%
  add_fcm_phase(
    fcs_column_name = "fsl_fcs_cat",
    rcsi_column_name = "fsl_rcsi_cat",
    hhs_column_name = "fsl_hhs_cat_ipc",
    fcs_categories_acceptable = "Acceptable",
    fcs_categories_poor = "Poor",
    fcs_categories_borderline = "Borderline",
    rcsi_categories_low = "No to Low",
    rcsi_categories_medium = "Medium",
    rcsi_categories_high = "High",
    hhs_categories_none = "None",
    hhs_categories_little = "No or Little",
    hhs_categories_moderate = "Moderate",
    hhs_categories_severe = "Severe",
    hhs_categories_very_severe = "Very Severe"
  )
df_with_fcm_1 %>%
  dplyr::select(uuid, fc_cell, fc_phase) %>%
  head(20)
```

### Example:: Add Food Consumption Matrix (FCM) using HDDS, RCSI, and HHS
**Notice that these functions are also pipable**
``` {r, eval=TRUE, warning=F}
df_with_fcm_2 <- df_with_hdds %>%
  add_fcm_phase(
    hdds_column_name = "fsl_hdds_cat",
    rcsi_column_name = "fsl_rcsi_cat",
    hhs_column_name = "fsl_hhs_cat_ipc",
    hdds_categories_low = "Low",
    hdds_categories_medium = "Medium",
    hdds_categories_high = "High",
    rcsi_categories_low = "No to Low",
    rcsi_categories_medium = "Medium",
    rcsi_categories_high = "High",
    hhs_categories_none = "None",
    hhs_categories_little = "No or Little",
    hhs_categories_moderate = "Moderate",
    hhs_categories_severe = "Severe",
    hhs_categories_very_severe = "Very Severe"
  )
df_with_fcm_2 %>%
  dplyr::select(uuid, fc_cell, fc_phase) %>%
  head(20)
```

### Example:: Add Food Consumption Matrix (FCM) using FCS and HHS
**Notice that these functions are also pipable**
``` {r, eval=TRUE, warning=F}
df_with_fcm_3 <- df_with_hdds %>%
  add_fcm_phase(
    fcs_column_name = "fsl_fcs_cat",
    hhs_column_name = "fsl_hhs_cat_ipc",
    fcs_categories_acceptable = "Acceptable",
    fcs_categories_poor = "Poor",
    fcs_categories_borderline = "Borderline",
    hhs_categories_none = "None",
    hhs_categories_little = "No or Little",
    hhs_categories_moderate = "Moderate",
    hhs_categories_severe = "Severe",
    hhs_categories_very_severe = "Very Severe"
  )
df_with_fcm_3 %>%
  dplyr::select(uuid, fc_cell, fc_phase) %>%
  head(20)
```

### Example:: Add Food Consumption Matrix (FCM) using HDDS and HHS
**Notice that these functions are also pipable**
``` {r, eval=TRUE, warning=F}
df_with_fcm_4 <- df_with_hdds %>%
  add_fcm_phase(
    hdds_column_name = "fsl_hdds_cat",
    hhs_column_name = "fsl_hhs_cat_ipc",
    hdds_categories_low = "Low",
    hdds_categories_medium = "Medium",
    hdds_categories_high = "High",
    hhs_categories_none = "None",
    hhs_categories_little = "No or Little",
    hhs_categories_moderate = "Moderate",
    hhs_categories_severe = "Severe",
    hhs_categories_very_severe = "Very Severe"
  )
df_with_fcm_4 %>%
  dplyr::select(uuid, fc_cell, fc_phase) %>%
  head(20)
```

### Example:: Add FEWSNET Food Consumption-Livelihood Matrix (FCLCM)
**Notice that these functions are also pipable**
``` {r, eval=TRUE, warning=F}
df_with_fclcm <- df_with_fcm_1 %>% ## Taken from previous Example
  add_fclcm_phase()
df_with_fclcm %>%
  dplyr::select(uuid, fclcm_phase) %>%
  head(20)
```


## Checking Flags (For Quality reports and Plausibility checks)

```{r include=T,eval=T}
tool <- impactR4PHU_survey_template
```

### Example:: Check Food Security and Livelihoods Flags 

``` {r, eval=TRUE, warning=F}
fsl_flags <- df_with_fclcm %>% 
  check_fsl_flags(tool.survey = tool,
                  grouping = "enumerator")
fsl_flags %>% 
  dplyr::select(uuid, group,starts_with("flag_")) %>% 
  head(20)
```


### Example:: Check WASH Flags 

``` {r, eval=TRUE, warning=F}
container_df <- impactR4PHU_data_wash_template
wash_flags <- df %>% 
  check_wash_flags(data_container_loop = container_df,
                   grouping = "enumerator")
wash_flags %>% 
  dplyr::select(uuid, group,starts_with("flag_")) %>% 
  head(20)
```

## Code of Conduct

Please note that the addindicators project is released with a [Contributor Code of Conduct](https://impact-initiatives.github.io/impactR4PHU/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
