---
title: "IPHRA Tabular Analysis"
subtitle: "`r strings['dataset.name.short']`"
date: "`r strings['out_date']`"
output: html_document
---

<style>
.tocify-subheader {
  font-size: 0.7em;
}
.tocify-item {
  font-size: 0.85em;
  padding-left: 25px;
  text-indent: 0;
}
</style>

```{r logo, echo=FALSE}
htmltools::img(src = knitr::image_uri("./../resources/Logo_Reach_RGB_1.png"), 
               alt = "REACH logo",
               style = 'position:absolute; top:0; right:0; padding:0; margin:20; width:250px')
```



```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
  options(scipen = 999)
  rm(list=ls()[!ls() %in% c("params", "strings", "language")])
  
  source("./../src/init.R")

  ##############################################################################################################

  ## FIX A FEW THINGS TO ALIGN DATA & TOOL WITH ANALYSIS SCRIPT
  
  source("./../src/fix_bugged_names.R")
  
  ## ADDING WEIGHTS, OVERALL AND GROUPING VARIABLES 

  source("./../src/format_dataset.R")  # <- additional indicators and grouping variables are added here 
  
  for(sheet in names(data.list)){
    data.list[[sheet]] <- data.list[[sheet]] %>% 
      mutate(overall = "overall",
             weight = 1) %>% 
      mutate_at(vars(everything()),~ifelse(. == "",NA,.))
  } 
  # all additional columns from data that need to be included in srvyr designs (need to be present in all sheets):
  special_vars <- c("overall", "weight", daf$admin) %>% unique  

```

```{r setup2, include=FALSE}

  ## FINAL TOUCHUPS TO DAF, CONVERTING COLUMNS
  ################################################################################
  
  ## a lookup tibble for variable/column names:
  var_lookup <- tibble()
  for (sheet in names(data.list)){
    var_lookup <- rbind(var_lookup, tibble(variable = names(data.list[[sheet]]), datasheet = sheet)) %>% 
      distinct(variable, .keep_all = T) %>% filter(stringr::str_detect(variable, "(/)|(___)", T))
                                                       # ^ here, I am assuming that no one will put a variable in the DAF that contains '/' or '___', or starts with '_'
        # also note that by using distinct here, if the same variable appears in multiple sheets, then by default the first sheet will be used (so: main usually)
  }
 # ADD DATASHEET COLUMN TO DAF
  if(!"datasheet" %in% names(daf)) daf <- daf %>% left_join(var_lookup, by = "variable")
  
  missing_sheets <- daf %>% filter(is.na(datasheet)) %>% pull(variable)
  if(length(missing_sheets) > 0) stop("These variables are missing from data: ", paste(missing_sheets))
  rm(missing_sheets)

 # CONVERT!
  source("./../src/convert_cols_with_daf.R")


  ## SRVYR DESIGNS
  ##############################################################################

  srvyr.designs  <- list()
  
  for(sheet in names(data.list)){
    daf_vars <- daf %>% filter(var_type != "select_multiple" & datasheet == sheet) %>% pull(variable)
  
    daf_vars_sm <- daf %>% filter(var_type == "select_multiple" & datasheet == sheet) %>% pull(variable)
    sm_vars_pattern <- paste0("^",paste0("(",daf_vars_sm,")", collapse = "|"))
    
    daf_disaggs <- daf %>% filter(!isna(disaggregations) & datasheet == sheet) %>% pull(disaggregations) %>% stringr::str_split(" *; *") %>% unlist %>% unique
    daf_disaggs <- daf_disaggs[daf_disaggs!=""]
    
    survey_data <- data.list[[sheet]] %>% select(all_of(special_vars), all_of(daf_vars), all_of(daf_disaggs), matches(sm_vars_pattern))
    
    srvyr.designs[[sheet]] <- srvyr::as_survey_design(survey_data, weights = NULL)
    
    rm(survey_data, daf_vars, daf_vars_sm, daf_disaggs)
  }

  
```

# {.tabset}

## Introduction


```{r, results='asis'}
if(language['language_assessment'] == "English"){
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What is this tool?"))
  cat('\nThe IPHRA Tabular Analysis is an analytical platform that presents a multitude of quantitative data tables. It encompasses a wide range of indicators collected through the IPHRA assessment process, empowering users to examine and interpret complex datasets effectively. This tool is structured to support understanding the distribution of your data and support you writing your factsheets/outputs/reports, and create other visualizations.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What is in this tool?"))
   cat('\nWithin this tool, users will find a wealth of information organized into distinct categories, each pertaining to critical aspects of humanitarian analysis:')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Household (HH) Demographics"))
  cat('\nExamine the composition and distribution of populations within households.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Individual (IND) Demographics"))
  cat('\nDelve into detailed demographic breakdowns at the individual level.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Healthcare"))
  cat('\nAccess data on healthcare availability, utilization, and specific health outcomes within communities on individual and household level.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "WASH"))
  cat('\nUnderstand the access and quality of WASH facilities and practices.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Shelter"))
  cat('\nReview information on the types and adequacy of shelter among the assessed population.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Child Nutrition"))
  cat('\nGet insights into the nutritional status and risk factors affecting children.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Women"))
  cat('\nFocus on gender-specific data that highlights the situation of women in the context of healthcare, nutrition, and risk.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Death"))
  cat('\nAnalyze rates and causes of death to gauge the health environment')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Food Security and Livelihood (FSL)"))
  cat('\nExplore data on food availability, accessibility, and livelihood resources.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Mortality"))
  cat('\nAssess overall mortality rates to understand broader health trends.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "MUAC/Nutrition"))
  cat('\nEvaluate nutritional status indicators, such as MUAC measurements, to determine the prevalence of malnutrition.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What else to know?"))
  cat('\nAs you saw in the output folder, you will have another excel file outputed from the analysis script. The Excel file includes 4 sheets. The first 2 are all the tables that you see in the different sections of this HTML output. You can navigate to respective tables through the first sheet "Table of Contents". The third sheet is nothing more than just the tables shown in the MUAC/Nutrition tab. The fourth tab is showing the Nutrition indices table disaggregated by sex and age. Please be aware of the footnote indication on the usage of the final percentages.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "Feedback"))
  cat('\nFeedback on improvements to this product can be done through reaching out to:\n\n-abraham.azar@impact-initiatives.org \n\n -impact.geneva.phu@impact-initiatives.org')
} else{
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "Qu'est-ce que cet outil?"))
  cat('\nL analyse tabulaire de l IPHRA est une plateforme analytique qui présente une multitude de tableaux de données quantitatives. Elle englobe un large éventail d indicateurs collectés dans le cadre du processus d évaluation de l IPHRA, permettant aux utilisateurs d examiner et d interpréter efficacement des ensembles de données complexes. Cet outil est structuré de manière à vous aider à comprendre la distribution de vos données et à vous aider à rédiger vos fiches/résultats/rapports et à créer d autres visualisations.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "Que contient cet outil?"))
  cat('\nDans cet outil, les utilisateurs trouveront une mine d informations organisées en catégories distinctes, chacune se rapportant à des aspects critiques de l analyse humanitaire :')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Données démographiques sur les ménages"))
  cat('\nExaminer la composition et la répartition des populations au sein des ménages.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Données démographiques individuelles (IND)"))
  cat('\nExaminez les compositions démographiques détaillées au niveau individuel.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Soins de santé"))
  cat('\nAccéder aux données sur la disponibilité et l utilisation des soins de santé, ainsi que sur les résultats spécifiques en matière de santé au sein des communautés, au niveau des individus et des ménages.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "WASH"))
  cat('\nComprendre l accès et la qualité des installations et des pratiques en matière d eau, d assainissement et d hygiène.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Abri"))
  cat('\nExaminer les informations relatives aux types et à l adéquation des abris de la population évaluée.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Child Nutrition"))
  cat('\nGet insights into the nutritional status and risk factors affecting children.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Femmes"))
  cat('\nSe concentrer sur les données sexospécifiques qui mettent en évidence la situation des femmes dans le contexte des soins de santé, de la nutrition et des risques.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "La mort"))
  cat('\nAnalyser les taux et les causes de décès pour évaluer l environnement sanitaire.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Sécurité alimentaire et moyens de subsistance (FSL)"))
  cat('\nExplorez les données relatives à la disponibilité et à l accessibilité de la nourriture, ainsi qu aux moyens de subsistance.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Mortalité"))
  cat('\nÉvaluer les taux de mortalité globaux pour comprendre les tendances générales en matière de santé.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "MUAC/Nutrition"))
  cat('\nÉvaluer les indicateurs de l état nutritionnel, tels que les mesures du MUAC, afin de déterminer la prévalence de la malnutrition.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "Que faut-il savoir de plus?"))
  cat('\nComme vous l avez vu dans le dossier de sortie, vous aurez un autre fichier Excel produit par le script d analyse. Le fichier Excel comprend 4 feuilles. Les deux premières sont toutes les tables que vous voyez dans les différentes sections de cette sortie HTML. Vous pouvez naviguer vers les tableaux respectifs à partir de la première feuille "Table des matières". La troisième feuille n est rien d autre que les tableaux figurant dans l onglet MUAC/Nutrition. Le quatrième onglet présente le tableau des indices nutritionnels ventilés par sexe et par âge. Veuillez tenir compte de la note de bas de page relative à l utilisation des pourcentages finaux.')
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "Commentaires"))
  cat('\nVous pouvez nous faire part de vos commentaires sur les améliorations à apporter à ce produit en nous contactant :\n\n- abraham.azar@impact-initiatives.org \n\n - impact.geneva.phu@impact-initiatives.org')
}
```


```{r, results='asis'}
sections <- daf %>% select(section) %>% distinct() %>% pull()

# produce HTML output: go line by line of the analysis flan and generate each section or table

for (i in sections){
  add_to_html.section(i)
  daf.section <- daf %>% filter(section == i)
  
  progress.bar.title <- as.character(Sys.time())
  pb <- tcltk::tkProgressBar(progress.bar.title, paste0("[", i, "] Number of entries executed"), 0, nrow(daf.section), 0, width = 500)
  
  for (r in 1:nrow(daf.section)){
    tcltk::setTkProgressBar(pb, r, progress.bar.title, paste0("[", i, "] Number of entries executed: ", r, " of ", nrow(daf.section)))
    
    # read entry from analysis flan
    entry <- load_entry(daf.section[r,])
    
    add_to_html.title(entry$label)
    cat(paste0("\n\nVariable name: <em><strong>", entry$variable),"</strong></em>")
    cat(entry$comments)
    
    # get the appropriate data source:
    srvyr.design <- srvyr.designs[[entry$datasheet]]
    
    # filter out NAs
    if(entry$omit_na) srvyr.design <- srvyr.design %>% filter(!is.na(!!sym(entry$variable)))
    
    # check if any data for this variable is left at all
    if(nrow(srvyr.design) == 0) {
      cat("\n\nNo data for this variable (all NA).\n")
      next
    }else{
      if(!entry$omit_na){
        cat(paste("\n\nIncluding NA values.\n"))
      }else{
        cat(paste("&emsp;|&emsp;",as_perc((nrow(srvyr.design))/nrow(data.list[[entry$datasheet]])),"of respondents answered this question.\n"))
      }
    }
    
    # group by admin:
    srvyr.design <- srvyr.design %>% group_by(!!sym(entry$admin))
    
    # loop through each disagg.var
    for (disagg.var in entry$disaggregate.variables) {
      if(!isna(disagg.var)) cat("\nDisaggregated by:<em><strong>", paste0(disagg.var),"</strong></em>")
      if(!is.na(disagg.var)){
        res <- make_table(srvyr.design, entry, disagg.var) %>% ungroup %>% select(-any_of("overall")) %>%
          filter(!is.na(disagg.var))
      } else {
        res <- make_table(srvyr.design, entry, disagg.var) %>% ungroup %>% select(-any_of("overall")) 
      }

      # add overall
      if(entry$admin != "overall"){
        entry.ovrl <- entry
        entry.ovrl$admin <- "overall"
        if(!"overall" %in% (srvyr.design %>% variable.names)) srvyr.design <- srvyr.design %>% mutate(overall = "overall")
        res.overall <- make_table(srvyr.design %>% ungroup %>% group_by(overall),
                                        entry.ovrl, disagg.var)  %>% 
          mutate(!!sym(entry$admin) := "overall") %>% 
          ungroup %>% select(-any_of("overall"))
        res <- res %>% bind_rows(res.overall) %>% distinct
      }
      # save the xlsx
      xlsx_name <- paste0(entry$xlsx_name, ifelse(isna(disagg.var), "", paste0("_by_", disagg.var)))
      writexl::write_xlsx(res, paste0(params["combine_folder"],"/",xlsx_name,".xlsx"))
    
      subch(DT::datatable(res, options = tableFormat))
    }
    
  }
  close(pb)
}

```

## FSL_Part2

```{r, results='asis'}
if(all(hdds_check_columns %in% names(main))) {
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>HDDS Groups</strong>"))
  subch(DT::datatable(hdds_table))
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>HDDS Category</strong>"))
  subch(DT::datatable(hdds_cat_table))
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>HDDS Score</strong>"))
  subch(DT::datatable(hdds_score_table))
}

if(all(hhs_check_columns %in% names(main))) {
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>HHS Groups</strong>"))
  subch(DT::datatable(hhs_table))
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>HHS Category</strong>"))
  subch(DT::datatable(hhs_cat_table))
}

if(all(fcs_check_columns %in% names(main))) {
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>FCS Groups</strong>"))
  subch(DT::datatable(fcs_table))
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>FCS Category</strong>"))
  subch(DT::datatable(fcs_cat_table))
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>FCS Score</strong>"))
  subch(DT::datatable(fcs_score_table))
}

if(all(rcsi_check_columns %in% names(main))) {
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>RCSI Groups</strong>"))
  subch(DT::datatable(rcsi_table))
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>RCSI Category</strong>"))
  subch(DT::datatable(rcsi_cat_table))
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>RCSI Score</strong>"))
  subch(DT::datatable(rcsi_score_table))
}

if(all(lcsi_check_columns %in% names(main))) {
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>LCSI Groups</strong>"))
  subch(DT::datatable(lcsi_table))
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>LCSI Category</strong>"))
  subch(DT::datatable(lcsi_cat_table))  
}

if(all(fcm_check_1_columns %in% names(main)) |
   all(fcm_check_2_columns %in% names(main)) |
   all(fcm_check_3_columns %in% names(main)) |
   all(fcm_check_4_columns %in% names(main)) |
   all(fcm_check_5_columns %in% names(main)) |
   all(fcm_check_6_columns %in% names(main))) {
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>FC Phase Groups</strong>"))
  subch(DT::datatable(fc_phase_table)) 
}

if(all(fclcm_check_columns %in% names(main))) {
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>FCLCM Phase Groups</strong>"))
  subch(DT::datatable(fclcm_phase_table)) 
}
```

```{r, results='asis'}

if(exists("results.summary")){
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",2), collapse=""), " ", "Mortality"))
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>Crude & UNDER 5 Overall</strong>"))
  DT::datatable(results.summary)
}
```

```{r, include=FALSE}
if(exists("results.summary")){
  plot_results.summary <- ggplot2::ggplot(results.summary %>% 
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5")), ggplot2::aes(x = variable)) + ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
    ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
    ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
    ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
    ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  
    ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
    ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
    ggplot2::scale_y_continuous(limits=c(0, under5$x_upp))+
    ggplot2::theme(legend.position = "none",
          axis.title.y = ggplot2::element_blank())+
    ggplot2::xlab("Overall HH Survey")+ 
    ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) + 
    ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))
}
```

```{r}
if(exists("results.summary")){
  plot_results.summary
}
```

```{r, results='asis'}
if(exists("results.summary_bySex")){
  cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "<strong>Crude & UNDER 5 by Sex</strong>"))
  subch(DT::datatable(results.summary_bySex))
}

```


```{r, include=FALSE}
if(exists("results.summary_bySex")){
  plot_results.summary_bySex <- ggplot2::ggplot(results.summary_bySex %>% 
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5")), ggplot2::aes(x = variable)) + ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
    ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
    ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
    ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
    ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  
    ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
    ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
    ggplot2::scale_y_continuous(limits=c(0, max(results.summary_bySex$`95%uci`)))+
    ggplot2::theme(legend.position = "none",
          axis.title.y = ggplot2::element_blank())+
    ggplot2::xlab("Overall HH Survey")+ 
    ggplot2::facet_wrap(~Sex)+
    ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) + 
    ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))
}
```

```{r}
if(exists("results.summary_bySex")){
  plot_results.summary_bySex
}
```

## MUAC / NUTRITION

```{r, include = FALSE}
nut <- nut %>% 
  mutate(fpc = nrow(hh_roster)/as.numeric(strings['population_estimation']))
if(as.numeric(strings['population_estimation']) > 10000){
  nut_survey <- srvyr::as_survey_design(nut)
} else {
  nut_survey <- srvyr::as_survey_design(nut,
                          fpc = fpc)
}

##Prevalence of acute malnutrition based on MUAC cut off's (and/or oedema) and by sex
proportions <- c("gam_muac_noflag","mam_muac_noflag","sam_muac_noflag")
results_prop <- data.frame()
for (i in proportions) {
  results2 <- nut_survey %>% 
    srvyr::summarise(num_sample = sum(!!rlang::sym(i), 
        na.rm = TRUE),
                     Prop = srvyr::survey_mean(!!rlang::sym(i), 
        na.rm = TRUE, vartype = "ci")) %>% 
    mutate(Name = i) %>% 
    relocate(Name, .before = 1)
  results_prop <- rbind(results_prop,results2)
}

results_prop <- results_prop %>% 
  mutate(Prop = paste0("(",num_sample,") ",round(Prop*100,2), " / [",round(Prop_low*100,2), " - ",round(Prop_upp * 100,2),"] (95% C.I.)")) %>% 
  select(-c(Prop_low,Prop_upp,num_sample)) %>% 
  rename(All = "Prop")
results_prop_sex <- data.frame()
for (i in proportions) {
  results2 <- nut_survey %>% 
    group_by(sex) %>% 
    srvyr::summarise(num_sample = sum(!!rlang::sym(i), 
        na.rm = TRUE),
                     Prop = srvyr::survey_mean(!!rlang::sym(i), 
        na.rm = TRUE, vartype = "ci")) %>% 
    mutate(Name = i,
           sex = case_when(sex == 1~"Male",
                           sex == 2~"Female")) %>% 
    relocate(Name, .before = 1)
  results_prop_sex <- rbind(results_prop_sex,results2)
}
results_prop_sex <- results_prop_sex %>% 
  mutate(Prop_low = ifelse(Prop_low<0,0,Prop_low)) %>% 
  mutate(Prop = paste0("(",num_sample,") ",round(Prop*100,2), " / [",round(Prop_low*100,2), " - ",round(Prop_upp * 100,2),"] (95% C.I.)")) %>% 
  select(-c(Prop_low,Prop_upp,num_sample)) %>% 
  tidyr::pivot_wider(names_from = sex, values_from = Prop)

results_prop_final <- results_prop %>% 
  left_join(results_prop_sex) %>% 
  mutate(AMN_MUAC_Indicator = case_when(Name == "gam_muac_noflag"~"Prevalence of global malnutrition\n(< 125 mm and/or oedema)",
                          Name == "mam_muac_noflag"~"Prevalence of moderate malnutrition\n(< 125 mm and >115 mm, no oedema)",
                          Name == "sam_muac_noflag"~"Prevalence of severe malnutrition\n(< 115 mm and/or oedema)")) %>% 
  select(-Name) %>% 
  relocate(AMN_MUAC_Indicator, .before= 1)
  


## Prevalence of acute malnutrition based on MUAC-for-age z-score cut off's (and/or oedema) and by sex
proportions <- c("global_mfaz_noflag","moderate_mfaz_noflag","severe_mfaz_noflag")
results_prop_mfaz <- data.frame()
for (i in proportions) {
  results2 <- nut_survey %>% 
    srvyr::summarise(num_sample = sum(!!rlang::sym(i), 
        na.rm = TRUE),
                     Prop = srvyr::survey_mean(!!rlang::sym(i), 
        na.rm = TRUE, vartype = "ci")) %>% 
    mutate(Name = i) %>% 
    relocate(Name, .before = 1)
  results_prop_mfaz <- rbind(results_prop_mfaz,results2)
}

results_prop_mfaz <- results_prop_mfaz %>% 
  mutate(Prop = paste0("(",num_sample,") ",round(Prop*100,2), " / [",round(Prop_low*100,2), " - ",round(Prop_upp * 100,2),"] (95% C.I.)")) %>% 
  select(-c(Prop_low,Prop_upp,num_sample)) %>% 
  rename(All = "Prop")
results_prop_mfaz_sex <- data.frame()
for (i in proportions) {
  results2 <- nut_survey %>% 
    group_by(sex) %>% 
    srvyr::summarise(num_sample = sum(!!rlang::sym(i), 
        na.rm = TRUE),
                     Prop = srvyr::survey_mean(!!rlang::sym(i), 
        na.rm = TRUE, vartype = "ci")) %>% 
    mutate(Name = i,
           sex = case_when(sex == 1~"Male",
                           sex == 2~"Female")) %>% 
    relocate(Name, .before = 1)
  results_prop_mfaz_sex <- rbind(results_prop_mfaz_sex,results2)
}
results_prop_mfaz_sex <- results_prop_mfaz_sex %>% 
  mutate(Prop_low = ifelse(Prop_low<0,0,Prop_low)) %>% 
  mutate(Prop = paste0("(",num_sample,") ",round(Prop*100,2), " / [",round(Prop_low*100,2), " - ",round(Prop_upp * 100,2),"] (95% C.I.)")) %>% 
  select(-c(Prop_low,Prop_upp,num_sample)) %>% 
  tidyr::pivot_wider(names_from = sex, values_from = Prop)

results_prop_final_mfaz <- results_prop_mfaz %>% 
  left_join(results_prop_mfaz_sex) %>% 
  mutate(AMN_MUAC_Indicator = case_when(Name == "severe_mfaz_noflag"~"Prevalence of severe malnutrition\n(< -3 MUAC-for-age z-score and/or oedema)",
                          Name == "moderate_mfaz_noflag"~"Prevalence of moderate malnutrition\n(>= -3 and < -2 MUAC-for-age z-score, no oedema)",
                          Name == "global_mfaz_noflag"~"Prevalence of global malnutrition\n(< -2 MUAC-for-age z-score and/or oedema)")) %>%  select(-Name) %>% 
  relocate(AMN_MUAC_Indicator, .before= 1)
  
mean <- c("muac_noflag","mfaz_noflag")

results_mean <- data.frame()

# results <- data.frame()
for (i in mean) {
  results2 <- nut_survey %>% 
    srvyr::summarise(Mean = srvyr::survey_mean(!!rlang::sym(i), 
        na.rm = TRUE, vartype = "ci")) %>% 
    mutate(Name = i) %>%
    mutate_at(vars(starts_with("Mean_")),~round(.,2)) %>% 
    relocate(Name, .before = 1)
  results_mean <- rbind(results_mean,results2)
}



##Prevalence of acute malnutrition based on MUAC cut off's (and/or oedema) and by Age_group
proportions <- c("gam_muac_noflag","mam_muac_noflag","sam_muac_noflag")
results_prop_age_group <- data.frame()
for (i in proportions) {
  results2 <- nut_survey %>% 
    mutate(age_group = as.character(cut(as.numeric(age_months), 
                                breaks = c(5,17,29,41,53,59),
                                labels = c("06-17", "18-29", "30-41", "42-53",
                                           "54-59")))) %>% 
    group_by(age_group) %>% 
    srvyr::summarise(num_sample = sum(!!rlang::sym(i), 
        na.rm = TRUE),
                     Prop = srvyr::survey_mean(!!rlang::sym(i), 
        na.rm = TRUE, vartype = "ci")) %>% 
    mutate(Name = i) %>% 
    relocate(Name, .before = 1)
  results_prop_age_group <- rbind(results_prop_age_group,results2)
}
## Total age_Group
age_group <- nut_survey %>% 
  mutate(age_group = as.character(cut(as.numeric(age_months), 
                              breaks = c(5,17,29,41,53,59),
                              labels = c("06-17", "18-29", "30-41", "42-53",
                                         "54-59")))) %>% 
  group_by(age_group) %>% 
  srvyr::summarise(Total = n()) %>% 
  filter(!is.na(age_group))

## calculate eodema
edema <- nut_survey %>% 
  mutate(age_group = as.character(cut(as.numeric(age_months), 
                              breaks = c(5,17,29,41,53,59),
                              labels = c("06-17", "18-29", "30-41", "42-53",
                                         "54-59")))) %>% 
  group_by(age_group) %>% 
  srvyr::summarise(edema_total = sum(flag_edema_pitting,na.rm=T)) %>% 
  filter(!is.na(age_group))

num_sample <- results_prop_age_group %>% 
  filter(!is.na(age_group)) %>% 
  group_by(age_group) %>% 
  summarise(num_sample = sum(num_sample,na.rm=T)) %>% 
  left_join(age_group) %>% 
  left_join(edema) %>% 
  mutate(Normal = paste0(Total-num_sample, " / ", round(((Total-num_sample)/Total) *100,2),"%")) %>% 
  mutate(Oedema = paste0(edema_total, " / ", round(((edema_total)/Total) *100,2),"%")) %>% 
  select(-c(num_sample,edema_total))


results_prop_age_group_final <- results_prop_age_group %>% 
  filter(!is.na(age_group)) %>% 
  mutate(Prop_low = ifelse(Prop_low<0,0,Prop_low)) %>% 
  mutate(Prop = paste0("(",num_sample,") ",round(Prop*100,2), " / [",round(Prop_low*100,2), " - ",round(Prop_upp * 100,2),"] (95% C.I.)")) %>% 
  select(-c(Prop_low,Prop_upp,num_sample))%>% 
  tidyr::pivot_wider(names_from = Name, values_from = Prop) %>% 
  left_join(num_sample) %>% 
  relocate(Total,.before = 2)

```

### Prevalence of acute malnutrition based on MUAC cut off's (and/or oedema) and by sex

```{r, results='asis'}
subch(DT::datatable(results_prop_final))
```

### Prevalence of acute malnutrition based on MUAC cut off's (and/or oedema) and by Age Group

```{r, results='asis'}
subch(DT::datatable(results_prop_age_group_final))
```

### Prevalence of acute malnutrition based on MUAC-for-age z-score cut off's (and/or oedema) and by sex

```{r, results='asis'}
subch(DT::datatable(results_prop_final_mfaz))
```

### Mean (MFAZ and MUAC)

```{r, results='asis'}
subch(DT::datatable(results_mean))
```


```{r, include=FALSE}
nut_assessment <- nut %>% 
  mutate(oedema_less_2 = ifelse(nut_edema_confirm == "yes"& age_months < 24,1,0),
         muac_115_less_2 = ifelse(nut_muac_cm<11.5 & age_months < 24,1,0),
         muac_115_124_less_2 = ifelse(nut_muac_cm>=11.5&nut_muac_cm<=12.4& age_months < 24,1,0),
         muac_125_less_2 = ifelse(nut_muac_cm>12.4& age_months < 24,1,0),
         oedema_more_2 = ifelse(nut_edema_confirm == "yes"& age_months >= 24,1,0),
         muac_115_more_2 = ifelse(nut_muac_cm<11.5 & age_months >= 24,1,0),
         muac_115_124_more_2 = ifelse(nut_muac_cm>=11.5&nut_muac_cm<=12.4& age_months >= 24,1,0),
         muac_125_more_2 = ifelse(nut_muac_cm>12.4& age_months >= 24,1,0),
         sex = case_when(sex == 1 ~ "Male",
                         sex == 2 ~ "Female")) %>% 
  group_by(sex) %>% 
  summarise(
    oedema_less_2 = sum(oedema_less_2,na.rm=T),
            muac_115_less_2 = sum(muac_115_less_2,na.rm=T),
            muac_115_124_less_2 = sum(muac_115_124_less_2,na.rm=T),
            muac_125_less_2 = sum(muac_125_less_2,na.rm=T),
            oedema_more_2 = sum(oedema_more_2,na.rm=T),
            muac_115_more_2 = sum(muac_115_more_2,na.rm=T),
            muac_115_124_more_2 = sum(muac_115_124_more_2,na.rm=T),
            muac_125_more_2 = sum(muac_125_more_2,na.rm=T)) 

trans_nut_assessment <- data.frame(t(nut_assessment))
names(trans_nut_assessment) <- trans_nut_assessment[1,]
trans_nut_assessment <- trans_nut_assessment %>% 
  relocate(Male,.before=1)
trans_nut_assessment <- trans_nut_assessment[-1,] %>% 
  mutate_at(vars(c(Male,Female)),as.numeric)

```

```{r message=TRUE, warning=FALSE, include=FALSE}
list_muac <- list("Prevalence of acute malnutrition based on MUAC cut off's (and/or oedema) and by sex" = results_prop_final,
                  "Prevalence of acute malnutrition based on MUAC cut off's (and/or oedema) and by Age Group" = results_prop_age_group_final,
                  "Prevalence of acute malnutrition based on MUAC-for-age z-score cut off's (and/or oedema) and by sex" = results_prop_final_mfaz,
                  "Mean (MFAZ and MUAC)" = results_mean)
## output XLSX files

file.list <- list.files(path = params['combine_folder'], pattern = "*.xlsx")
file.list <- setNames(file.list, paste0(params['combine_folder'], file.list))
df <- lapply(names(file.list), readxl::read_excel)
names(df) <- stringr::str_remove(file.list, ".xlsx")

sorted_df <- df

save.dfs(sorted_df,list_muac,trans_nut_assessment, paste0("./../output/", strings['dataset.name.short'], "_combined_analysis_toc_", strings['out_date'], ".xlsx"), use_template = T)

for (i in 1:length(names(sorted_df))){
  if (nchar(names(sorted_df)[i]) > 31){
    names(sorted_df)[i] <- stringr::str_trunc(names(sorted_df)[i], 28)
    names(sorted_df)[i] <- paste0(names(sorted_df)[i],i)
  } else{
    names(sorted_df) <- names(sorted_df)
  }
}

```



