---
title: "Mortality Descriptive Analysis Report"
subtitle: "`r Sys.Date()`"
output: html_document
---

<style>
.tocify-subheader {
  font-size: 0.7em;
}
.tocify-item {
  font-size: 0.85em;
  padding-left: 25px;
  text-indent: 0;
}
</style>


```{r logo, echo=FALSE}
htmltools::img(src = knitr::image_uri("resources/Logo_Reach_RGB_1.png"),
               alt = "REACH logo",
               style = 'position:absolute; top:0; right:0; padding:0; margin:20; width:250px')
```



```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
  options(scipen = 999)
  rm(list=ls()[!ls() %in% c("params", "strings", "language")])
  
  source("src/init.R")

  ##############################################################################################################

  ## FIX A FEW THINGS TO ALIGN DATA & TOOL WITH ANALYSIS SCRIPT
  
  source("src/fix_bugged_names.R")
  
  ## ADDING WEIGHTS, OVERALL AND GROUPING VARIABLES 

  source("src/format_dataset.R")  # <- additional indicators and grouping variables are added here 
  

  # all additional columns from data that need to be included in srvyr designs (need to be present in all sheets):
  special_vars <- c("overall", "weight", daf$admin) %>% unique  

```

```{r setup2, include=FALSE}

  ## FINAL TOUCHUPS TO DAF, CONVERTING COLUMNS
  ################################################################################
  if(nrow(daf)>0){
    
    ## a lookup tibble for variable/column names:
    var_lookup <- tibble()
    for (sheet in names(data.list)){
      var_lookup <- rbind(var_lookup, tibble(variable = names(data.list[[sheet]]), datasheet = sheet)) %>% 
        distinct(variable, .keep_all = T) %>% filter(stringr::str_detect(variable, "(/)|(___)", T))
                                                         # ^ here, I am assuming that no one will put a variable in the DAF that contains '/' or '___', or starts with '_'
          # also note that by using distinct here, if the same variable appears in multiple sheets, then by default the first sheet will be used (so: main usually)
    }
   # ADD DATASHEET COLUMN TO DAF
    if(!"datasheet" %in% names(daf)) daf <- daf %>% left_join(var_lookup, by = "variable")
    
    missing_sheets <- daf %>% filter(is.na(datasheet)) %>% pull(variable)
    if(length(missing_sheets) > 0) stop("These variables are missing from data: ", paste(missing_sheets))
    rm(missing_sheets)
  
   # CONVERT!
    source("src/convert_cols_with_daf.R")
  
  
    ## SRVYR DESIGNS
    ##############################################################################
  
    srvyr.designs  <- list()
    
    for(sheet in names(data.list)){
      daf_vars <- daf %>% filter(var_type != "select_multiple" & datasheet == sheet) %>% pull(variable)
    
      daf_vars_sm <- daf %>% filter(var_type == "select_multiple" & datasheet == sheet) %>% pull(variable)
      sm_vars_pattern <- paste0("^",paste0("(",daf_vars_sm,")", collapse = "|"))
      
      daf_disaggs <- daf %>% filter(!isna(disaggregations) & datasheet == sheet) %>% pull(disaggregations) %>% stringr::str_split(" *; *") %>% unlist %>% unique
      daf_disaggs <- daf_disaggs[daf_disaggs!=""]
      
      survey_data <- data.list[[sheet]] %>% select(all_of(special_vars), all_of(daf_vars), all_of(daf_disaggs), matches(sm_vars_pattern))
      
      srvyr.designs[[sheet]] <- srvyr::as_survey_design(survey_data, weights = weight)
      
      rm(survey_data, daf_vars, daf_vars_sm, daf_disaggs)
    }
  }

  
```

# {.tabset .tabset-fade}

## Introduction

```{r, results='asis'}
cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What is this tool?"))
cat('\nThe Mortality Descriptive Analysis is an analytical platform that presents a multitude of quantitative data tables. It encompasses a wide range of Mortality indicators collected through the assessment process, empowering users to examine and interpret complex datasets effectively. This tool is structured to support understanding the distribution of your data and support you writing your factsheets/outputs/reports, and create other visualizations.')
cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What is in this tool?"))
cat('\nWithin this tool, users will find a wealth of information organized into distinct categories, each pertaining to critical aspects of humanitarian analysis:')
cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Mortality"))
cat('\nExplore data on Mortality.')
cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What else to know?"))
cat('\nAs you saw in the output folder, you will have another excel file outputed from the analysis script. The Excel file includes 2 sheets. The first 2 are all the tables that you see in the different sections of this HTML output. You can navigate to respective tables through the first sheet "Table of Contents".')
cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "Feedback"))
cat('\nFeedback on improvements to this product can be done through reaching out to:\n\n-abraham.azar@impact-initiatives.org \n\n -impact.geneva.phu@impact-initiatives.org')
```


```{r, results='asis'}
if(nrow(daf)>0){
  
  sections <- daf %>% select(section) %>% distinct() %>% pull()
  
  # produce HTML output: go line by line of the analysis flan and generate each section or table
  
  for (i in sections){
    add_to_html.section(i)
    daf.section <- daf %>% filter(section == i)
    
    progress.bar.title <- as.character(Sys.time())
    pb <- tcltk::tkProgressBar(progress.bar.title, paste0("[", i, "] Number of entries executed"), 0, nrow(daf.section), 0, width = 500)
    
    for (r in 1:nrow(daf.section)){
      tcltk::setTkProgressBar(pb, r, progress.bar.title, paste0("[", i, "] Number of entries executed: ", r, " of ", nrow(daf.section)))
      
      # read entry from analysis flan
      entry <- load_entry(daf.section[r,])
      
      add_to_html.title(entry$label)
      cat(paste0("\n\nVariable name: <em><strong>", entry$variable),"</strong></em>")
      cat(entry$comments)
      
      # get the appropriate data source:
      srvyr.design <- srvyr.designs[[entry$datasheet]]
      
      # filter out NAs
      if(entry$omit_na) srvyr.design <- srvyr.design %>% filter(!is.na(!!sym(entry$variable)))
      
      # check if any data for this variable is left at all
      if(nrow(srvyr.design) == 0) {
        cat("\n\nNo data for this variable (all NA).\n")
        next
      }else{
        if(!entry$omit_na){
          cat(paste("\n\nIncluding NA values.\n"))
        }else{
          cat(paste("&emsp;|&emsp;",as_perc((nrow(srvyr.design))/nrow(data.list[[entry$datasheet]])),"of respondents answered this question.\n"))
        }
      }
      
      # group by admin:
      srvyr.design <- srvyr.design %>% group_by(!!sym(entry$admin))
      
      # loop through each disagg.var
      for (disagg.var in entry$disaggregate.variables) {
        if(!isna(disagg.var)) cat("\nDisaggregated by:<em><strong>", paste0(disagg.var),"</strong></em>")
        if(!is.na(disagg.var)){
          res <- make_table(srvyr.design, entry, disagg.var) %>% ungroup %>% select(-any_of("overall")) %>%
            filter(!is.na(disagg.var))
        } else {
          res <- make_table(srvyr.design, entry, disagg.var) %>% ungroup %>% select(-any_of("overall")) 
        }
  
        # add overall
        if(entry$admin != "overall"){
          entry.ovrl <- entry
          entry.ovrl$admin <- "overall"
          if(!"overall" %in% (srvyr.design %>% variable.names)) srvyr.design <- srvyr.design %>% mutate(overall = "overall")
          res.overall <- make_table(srvyr.design %>% ungroup %>% group_by(overall),
                                          entry.ovrl, disagg.var)  %>% 
            mutate(!!sym(entry$admin) := "overall") %>% 
            ungroup %>% select(-any_of("overall"))
          res <- res %>% bind_rows(res.overall) %>% distinct
        }
        # save the xlsx
        xlsx_name <- paste0(entry$xlsx_name, ifelse(isna(disagg.var), "", paste0("_by_", disagg.var)))
        writexl::write_xlsx(res, paste0(params["combine_folder"],"/",xlsx_name,".xlsx"))
      
        subch(DT::datatable(res, options = tableFormat))
      }
      
    }
    close(pb)
  }
}

```

```{r message=TRUE, warning=FALSE, include=FALSE}
teams_df <- data.list$main %>% 
  dplyr::select(uuid_main, team) %>% 
  dplyr::rename("uuid" = uuid_main)

weight_df <- data.list$main %>% 
  dplyr::select(uuid_main, weight) %>% 
  dplyr::rename("uuid" = uuid_main)

df_mortality_long <- df_mortality_long %>% 
  dplyr::left_join(teams_df)

```

## Mortality [Part 2] {.tabset .tabset-fade}

### Demographics {.tabset .tabset-fade}

#### Age pyramid in years disaggregated by gender 

```{r, message=FALSE}
impactR4PHU::plot_age_pyramid(df_mortality_long %>% 
                                  filter(is.na(left),
                                         is.na(death)))
```

#### Age pyramid in years disaggregated by gender per Team

```{r, results='asis', echo=FALSE}
if(yes_no_team == "yes"){
    list_teams <- raw.main[[team]] %>% unique()
    for (i in list_teams) {
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong> {.tabset .tabset-fade}"))
      list_enum <- raw.main %>% 
        dplyr::filter(!!rlang::sym(team) %in% i) %>% 
        dplyr::pull(!!rlang::sym(enumerator))%>% 
        unique()
      for (j in list_enum){
        cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",6), collapse=""), " ", "<strong>",j,"</strong>"))
        subch(impactR4PHU::plot_age_pyramid(df_mortality_long %>% 
                                              dplyr::filter(is.na(left),
                                                            is.na(death),
                                                            !!rlang::sym("enumerator") %in% j,
                                                            !!rlang::sym(team) %in% i)),
            fig_height = 5, fig_width = 7)
      }
    }
} else {
    list_enum <- df_mortality_long[["enumerator"]]%>% unique
    for (i in list_enum) {
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>Enumerator: ",i,"</strong>"))
      subch(impactR4PHU::plot_age_pyramid(df_mortality_long %>% 
                                      dplyr::filter(is.na(left),
                                             is.na(death),
                                             !!rlang::sym("enumerator") %in% i)),
            fig_height = 5, fig_width = 7)
    }
  }

```

#### Histogram of age in years

```{r, message=FALSE}

  impactR4PHU::plot_age_distribution(df_mortality_long %>%
                                       filter(is.na(left),
                                              is.na(death)),
                                     year_or_month = "year",
                                     max_age = 10)

```

#### Histogram of age in years per Team

```{r, results='asis', message=FALSE}
if(yes_no_team == "yes"){
    list_teams <- raw.main[[team]] %>% unique()
    for (i in list_teams) {
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong> {.tabset .tabset-fade}"))
      list_enum <- raw.main %>% 
        dplyr::filter(!!rlang::sym(team) %in% i) %>% 
        dplyr::pull(!!rlang::sym(enumerator))%>% 
        unique()
       for (j in list_enum){
          cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",6), collapse=""), " ", "<strong>",j,"</strong>"))
          subch(impactR4PHU::plot_age_distribution(df_mortality_long %>%
                                               filter(is.na(left),
                                                      is.na(death),
                                                      enumerator %in% j,
                                                      !!rlang::sym(team) %in% i),
                                             year_or_month = "year",
                                             max_age = 10),
                fig_height = 8)
       }
    }
} else {
    subch(impactR4PHU::plot_age_distribution(df_mortality_long %>%
                                       filter(is.na(left),
                                              is.na(death)),
                                     year_or_month = "year",
                                     max_age = 10,
                                     by_group = "enumerator"),
                fig_height = length(list_enum) * 2)
  }
```

#### Histogram of age in months

```{r, fig.width = 10, warning=FALSE, message=FALSE}
  impactR4PHU::plot_age_distribution(raw.hh_roster,
                                     year_or_month = "month",
                                     age_months = age_roster_month,
                                     breaks = 1)

```

#### Histogram of age in months per Team

```{r, results='asis',  warning=FALSE}
if(yes_no_team == "yes"){
    for (i in list_teams) {
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong> {.tabset .tabset-fade}"))
      plot_raw.main <- raw.main %>%
        dplyr::rename(uuid = uuid_main) %>%
        dplyr::filter(!!rlang::sym(team) == i)

      plot_raw.hh_roster <- raw.hh_roster %>%
        dplyr::rename(uuid = uuid_roster) %>%
        dplyr::filter(uuid %in% plot_raw.main$uuid)
      list_enum <- raw.main %>% 
        dplyr::filter(!!rlang::sym(team) %in% i) %>% 
        dplyr::pull(!!rlang::sym(enumerator))%>% 
        unique()
      if(enumerator %in% names(plot_raw.hh_roster)){
        for (j in list_enum){
          cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",6), collapse=""), " ", "<strong>",j,"</strong>"))
          subch(impactR4PHU::plot_age_distribution(plot_raw.hh_roster  %>%
                                               dplyr::filter(!!rlang::sym(enumerator) == j,
                                                            !!rlang::sym(team) %in% i),
                                               year_or_month = "month",
                                               age_months = age_roster_month,
                                               breaks = 1),
                fig_height = 8, fig_width = 10)
        }
      } else {
        for (j in list_enum){
          cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",6), collapse=""), " ", "<strong>",j,"</strong>"))
          subch(impactR4PHU::plot_age_distribution(plot_raw.hh_roster %>%
                                               dplyr::left_join(select(plot_raw.main, c("uuid", enumerator))) %>%
                                               dplyr::filter(!!rlang::sym(enumerator) == j),
                                               year_or_month = "month",
                                               age_months = age_roster_month,
                                               breaks = 1),
                fig_height = 8, fig_width = 10)
        }
      }
    }
} else {
  plot_raw.hh_roster <- raw.hh_roster %>%
    dplyr::rename(uuid = uuid_roster)
  plot_raw.main <- raw.main %>%
    dplyr::rename(uuid = uuid_main)
  if(enumerator %in% names(plot_raw.hh_roster)){
    subch(impactR4PHU::plot_age_distribution(plot_raw.hh_roster,
                                             year_or_month = "month",
                                             by_group = enumerator,
                                             age_months = age_roster_month,
                                             breaks = 1),
          fig_height = length(list_enum) * 2, fig_width = 10)
  } else {
    subch(impactR4PHU::plot_age_distribution(plot_raw.hh_roster %>%
                                               dplyr::left_join(select(plot_raw.main, c("uuid", enumerator))),
                                             year_or_month = "month",
                                             by_group = enumerator,
                                             age_months = age_roster_month,
                                             breaks = 1),
          fig_height = length(list_enum) * 2, fig_width = 10)
  }
}
```

### Results

#### Number of Death/Joiners/Leavers & Person Time per Enumerator

```{r, results='asis'}
if(yes_no_team == "yes"){
  for (i in list_teams) {
    cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong> {.tabset}"))
    table_djl_enum <- df_mortality_long %>%
      dplyr::filter(!!rlang::sym(team) %in% i) %>% 
      dplyr::group_by(enumerator) %>%
      dplyr::summarise(Leavers = sum(as.numeric(left), na.rm = T),
                       Joiners = sum(as.numeric(join), na.rm = T),
                       Death = sum(as.numeric(death), na.rm = T),
                       `Death Under 5` = sum(as.numeric(death_under5), na.rm = T),
                       `Person Time` = sum(as.numeric(person_time), na.rm = T),
                       `Person Time Under 5` = sum(as.numeric(under_5_pt), na.rm = T))

    total <- table_djl_enum %>%
      dplyr::group_by() %>%
      dplyr::summarise(Leavers = sum(as.numeric(Leavers), na.rm = T),
                       Joiners = sum(as.numeric(Joiners), na.rm = T),
                       Death = sum(as.numeric(Death), na.rm = T),
                       `Death Under 5` = sum(as.numeric(`Death Under 5`), na.rm = T),
                       `Person Time` = sum(as.numeric(`Person Time`), na.rm = T),
                       `Person Time Under 5` = sum(as.numeric(`Person Time Under 5`), na.rm = T)) %>%
      dplyr::mutate(enumerator = "Total") %>%
      dplyr::relocate(enumerator, .before = 1)
      
    table_djl_enum <- bind_rows(table_djl_enum, total)
    subch(DT::datatable(table_djl_enum))
  }
} else {
    table_djl_enum <- df_mortality_long %>%
      dplyr::group_by(enumerator) %>%
      dplyr::summarise(Leavers = sum(as.numeric(left), na.rm = T),
                       Joiners = sum(as.numeric(join), na.rm = T),
                       Death = sum(as.numeric(death), na.rm = T),
                       `Death Under 5` = sum(as.numeric(death_under5), na.rm = T),
                       `Person Time` = sum(as.numeric(person_time), na.rm = T),
                       `Person Time Under 5` = sum(as.numeric(under_5_pt), na.rm = T))

    total <- table_djl_enum %>%
      dplyr::group_by() %>%
      dplyr::summarise(Leavers = sum(as.numeric(Leavers), na.rm = T),
                       Joiners = sum(as.numeric(Joiners), na.rm = T),
                       Death = sum(as.numeric(Death), na.rm = T),
                       `Death Under 5` = sum(as.numeric(`Death Under 5`), na.rm = T),
                       `Person Time` = sum(as.numeric(`Person Time`), na.rm = T),
                       `Person Time Under 5` = sum(as.numeric(`Person Time Under 5`), na.rm = T)) %>%
      dplyr::mutate(enumerator = "Total") %>%
      dplyr::relocate(enumerator, .before = 1)
      
    table_djl_enum <- bind_rows(table_djl_enum, total)
    DT::datatable(table_djl_enum)
}


```

#### Rates {.tabset .tabset-fade}

##### Overall Mortality

```{r, include=FALSE}

srvey_mortality <- srvyr::as_survey_design(df_mortality_long %>%
                                                             dplyr::mutate(death = ifelse(is.na(death),0,as.numeric(death)),
                                                                           person_time = as.numeric(person_time),
                                                                           death_under5 = ifelse(is.na(death_under5),0,as.numeric(death_under5)),
                                                                           under_5_pt = ifelse(is.na(under_5_pt),0,as.numeric(under_5_pt))) %>% 
                                             dplyr::left_join(weight_df),
                                           weights = weight)
  
  crude <- srvey_mortality %>%
    srvyr::summarise(x = srvyr::survey_ratio(numerator = death * 10000,
                                             denominator = person_time,
                                             vartype = "ci")) %>%
    dplyr::mutate_at(vars(c(x,x_low,x_upp)),~round(.,2)) %>%
    dplyr::mutate(variable = "cmr")
  under_5 <- srvey_mortality %>%
    srvyr::summarise(x = srvyr::survey_ratio(numerator = death_under5 * 10000,
                                             denominator = under_5_pt,
                                             vartype = "ci"))%>%
    dplyr::mutate_at(vars(c(x,x_low,x_upp)),~round(.,2)) %>%
    mutate(variable = "u5mr")
  overall <- rbind(crude,under_5) %>%
   rename(`point.est` = "x",
          `95%lci` = "x_low",
          `95%uci` = "x_upp") %>%
   relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(overall)
```

```{r, include=FALSE}
plot_results.summary <- ggplot2::ggplot(overall %>%
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5")), ggplot2::aes(x = variable)) +
  ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
  ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(overall$`95%uci`)<2){
    2
  } else {
    max(overall$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Mortality Rates")+
  ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) +
  ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))
```

```{r}
plot_results.summary
```


##### By Gender Mortality

```{r, include=FALSE}
crude_gender <- results_mort_gender %>%
  dplyr::mutate(`point.est` = as.numeric(cdr),
                `95%lci` = as.numeric(stringr::str_extract(cdr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(cdr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group, `point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "cmr",
                group = case_when(group == 1~"Male",
                                  group == 2~"Female"))

under5_gender <- results_mort_gender %>%
  dplyr::mutate(`point.est` = as.numeric(u5dr),
                `95%lci` = as.numeric(stringr::str_extract(u5dr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(u5dr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group,`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "u5mr",
                group = case_when(group == 1~"Male",
                                  group == 2~"Female"))

by_gender <- rbind(crude_gender,under5_gender) %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(by_gender)
```

```{r, include=FALSE}
plot_results.summary_gender <- ggplot2::ggplot(by_gender %>%
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5")), ggplot2::aes(x = variable)) +
  ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
  ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(by_gender$`95%uci`)<2){
    2
  } else {
    max(by_gender$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Mortality Rates")+
  ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) +
  ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))+
  ggplot2::facet_wrap(~group)
```

```{r}
plot_results.summary_gender
```

##### By Age Group Mortality

```{r, include=FALSE}
crude_age_group <- results_mort_age_group %>%
  dplyr::mutate(`point.est` = as.numeric(cdr),
                `95%lci` = as.numeric(stringr::str_extract(cdr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(cdr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group, `point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "cmr",
                group = case_when(group == 1~"0-17",
                                  group == 2~"18-59",
                                  group == 3~"60+"))

by_age_group <- rbind(crude_age_group) %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(by_age_group)
```

```{r, include=FALSE}
plot_results.summary_age_group <- ggplot2::ggplot(by_age_group %>%
                                               mutate(variable = case_when(variable == "cmr"~"Crude")), ggplot2::aes(x = variable)) +
  ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
  ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(by_age_group$`95%uci`)<2){
    2
  } else {
    max(by_age_group$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Mortality Rates")+
  ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) +
  ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))+
  ggplot2::facet_wrap(~group)
```

```{r}
plot_results.summary_age_group
```

##### By Population Group Mortality

```{r, include=FALSE}
crude_pop_group <- results_mort_pop_group %>%
  dplyr::mutate(`point.est` = as.numeric(cdr),
                `95%lci` = as.numeric(stringr::str_extract(cdr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(cdr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group, `point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "cmr")

under5_pop_group <- results_mort_pop_group %>%
  dplyr::mutate(`point.est` = as.numeric(u5dr),
                `95%lci` = as.numeric(stringr::str_extract(u5dr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(u5dr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group,`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "u5mr")

by_pop_group <- rbind(crude_pop_group,under5_pop_group) %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(by_pop_group)
```

```{r, include=FALSE}
plot_results.summary_pop_group <- ggplot2::ggplot(by_pop_group %>%
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5")), ggplot2::aes(x = variable)) +
  ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
  ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(by_pop_group$`95%uci`)<2){
    2
  } else {
    max(by_pop_group$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Mortality Rates")+
  ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) +
  ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))+
  ggplot2::facet_wrap(~group)
```

```{r, fig.height=8, fig.width=7}
plot_results.summary_pop_group
```

##### By Admin 1 Mortality

```{r, include=FALSE}
if(is.null(cluster)){
  srvey_mortality <- srvyr::as_survey_design(df_mortality_long %>%
                                                             dplyr::mutate(death = ifelse(is.na(death),0,as.numeric(death)),
                                                                           person_time = as.numeric(person_time),
                                                                           death_under5 = ifelse(is.na(death_under5),0,as.numeric(death_under5)),
                                                                           under_5_pt = ifelse(is.na(under_5_pt),0,as.numeric(under_5_pt))))
  
  crude_admin1 <- srvey_mortality %>%
    dplyr::group_by(admin1) %>%
    srvyr::summarise(x = srvyr::survey_ratio(numerator = death * 10000,
                                             denominator = person_time,
                                             vartype = "ci")) %>%
    dplyr::mutate_at(vars(c(x,x_low,x_upp)),~round(.,2)) %>%
    dplyr::mutate(variable = "cmr")
  under_5_admin1 <- srvey_mortality %>%
    dplyr::group_by(admin1) %>%
    srvyr::summarise(x = srvyr::survey_ratio(numerator = death_under5 * 10000,
                                             denominator = under_5_pt,
                                             vartype = "ci"))%>%
    dplyr::mutate_at(vars(c(x,x_low,x_upp)),~round(.,2)) %>%
    mutate(variable = "u5mr")
  by_admin1 <- rbind(crude_admin1,under_5_admin1) %>%
   rename(`point.est` = "x",
          `95%lci` = "x_low",
          `95%uci` = "x_upp") %>%
   relocate(variable, .before = 1)
} else {
  srvey_mortality <- srvyr::as_survey_design(df_mortality_long %>%
                                                             dplyr::mutate(death = ifelse(is.na(death),0,as.numeric(death)),
                                                                           person_time = as.numeric(person_time),
                                                                           death_under5 = ifelse(is.na(death_under5),0,as.numeric(death_under5)),
                                                                           under_5_pt = ifelse(is.na(under_5_pt),0,as.numeric(under_5_pt))) %>% 
                                               dplyr::filter(!is.na(cluster)), 
                                             ids = cluster)
  
  crude_admin1 <- srvey_mortality %>%
    dplyr::group_by(admin1) %>%
    srvyr::summarise(x = srvyr::survey_ratio(numerator = death * 10000,
                                             denominator = person_time,
                                             vartype = "ci",
                                             deff = "replace")) %>%
    dplyr::mutate_at(vars(c(x,x_low,x_upp,x_deff)),~round(.,2)) %>%
    dplyr::mutate(variable = "cmr")
  under_5_admin1 <- srvey_mortality %>%
    dplyr::group_by(admin1) %>%
    srvyr::summarise(x = srvyr::survey_ratio(numerator = death_under5 * 10000,
                                             denominator = under_5_pt,
                                             vartype = "ci",
                                             deff = "replace"))%>%
    dplyr::mutate_at(vars(c(x,x_low,x_upp,x_deff)),~round(.,2)) %>%
    dplyr::mutate(variable = "u5mr")
  by_admin1 <- rbind(crude_admin1,under_5_admin1) %>%
    dplyr::mutate(x_deff = ifelse(is.nan(x_deff),0,x_deff)) %>% 
   dplyr::rename(`point.est` = "x",
          `95%lci` = "x_low",
          `95%uci` = "x_upp",
          `Design effect` = "x_deff") %>%
   dplyr::relocate(variable, .before = 1)
    
}
```

```{r, results='asis'}
DT::datatable(by_admin1)
```

```{r, include=FALSE}
plot_results.summary_admin1 <- ggplot2::ggplot(by_admin1 %>%
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5")), ggplot2::aes(x = variable)) +
  ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
  ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(by_admin1$`95%uci`)<2){
    2
  } else {
    max(by_admin1$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Mortality Rates")+
  ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) +
  ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))+
  ggplot2::facet_wrap(~admin1)
```

```{r}
plot_results.summary_admin1
```


##### By Admin 2 Mortality

```{r, include=FALSE}
crude_admin2 <- results_mort_admin2 %>%
  dplyr::mutate(`point.est` = as.numeric(cdr),
                `95%lci` = as.numeric(stringr::str_extract(cdr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(cdr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group, `point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "cmr")

under5_admin2 <- results_mort_admin2 %>%
  dplyr::mutate(`point.est` = as.numeric(u5dr),
                `95%lci` = as.numeric(stringr::str_extract(u5dr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(u5dr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group,`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "u5mr")

by_admin2 <- rbind(crude_admin2,under5_admin2) %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(by_admin2)
```

```{r, include=FALSE}
plot_results.summary_admin2 <- ggplot2::ggplot(by_admin2 %>%
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5")), ggplot2::aes(x = variable)) +
  ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
  ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(by_admin2$`95%uci`)<2){
    2
  } else {
    max(by_admin2$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Mortality Rates")+
  ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) +
  ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))+
  ggplot2::facet_wrap(~group)
```

```{r, fig.height=8,fig.width=7}
plot_results.summary_admin2
```

##### By Admin 1 by Population Group Mortality

```{r, include=FALSE}
crude_admin1_pop_group <- results_mort_admin1_pop_group %>%
  dplyr::mutate(`point.est` = as.numeric(cdr),
                `95%lci` = as.numeric(stringr::str_extract(cdr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(cdr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group, `point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "cmr")

under5_admin1_pop_group <- results_mort_admin1_pop_group %>%
  dplyr::mutate(`point.est` = as.numeric(u5dr),
                `95%lci` = as.numeric(stringr::str_extract(u5dr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(u5dr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group,`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "u5mr")

by_admin1_pop_group <- rbind(crude_admin1_pop_group,under5_admin1_pop_group) %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(by_admin1_pop_group)
```

```{r, include=FALSE}
plot_results.summary_admin1_pop_group <- ggplot2::ggplot(by_admin1_pop_group %>%
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5")), ggplot2::aes(x = variable)) +
  ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
  ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(by_admin1_pop_group$`95%uci`)<2){
    2
  } else {
    max(by_admin1_pop_group$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Mortality Rates")+
  ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) +
  ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))+
  ggplot2::facet_wrap(~group)
```

```{r, fig.height=8,fig.width=7}
plot_results.summary_admin1_pop_group
```


##### By HoH Gender Mortality

```{r, include=FALSE}
crude_hoh_gender <- results_mort_hoh_gender %>%
  dplyr::mutate(`point.est` = as.numeric(cdr),
                `95%lci` = as.numeric(stringr::str_extract(cdr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(cdr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group, `point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "cmr")

under5_hoh_gender <- results_mort_hoh_gender %>%
  dplyr::mutate(`point.est` = as.numeric(u5dr),
                `95%lci` = as.numeric(stringr::str_extract(u5dr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(u5dr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group,`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "u5mr")

by_hoh_gender <- rbind(crude_hoh_gender,under5_hoh_gender) %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(by_hoh_gender)
```

```{r, include=FALSE}
plot_results.summary_hoh_gender <- ggplot2::ggplot(by_hoh_gender %>%
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5")), ggplot2::aes(x = variable)) +
  ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
  ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(by_hoh_gender$`95%uci`)<2){
    2
  } else {
    max(by_hoh_gender$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Mortality Rates")+
  ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) +
  ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))+
  ggplot2::facet_wrap(~group)
```

```{r, fig.height=8,fig.width=7}
plot_results.summary_hoh_gender
```

##### By Income Source Mortality

```{r, include=FALSE}
crude_income_source <- results_mort_income_source %>%
  dplyr::mutate(`point.est` = as.numeric(cdr),
                `95%lci` = as.numeric(stringr::str_extract(cdr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(cdr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group, `point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "cmr")

under5_income_source <- results_mort_income_source %>%
  dplyr::mutate(`point.est` = as.numeric(u5dr),
                `95%lci` = as.numeric(stringr::str_extract(u5dr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(u5dr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group,`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "u5mr")

by_income_source <- rbind(crude_income_source,under5_income_source) %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(by_income_source)
```

```{r, include=FALSE}
plot_results.summary_income_source <- ggplot2::ggplot(by_income_source %>%
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5"),
                                                      group = factor(group, c("Below 20%", "20% - 40%","40% - 60%","60% - 80%","Above 80%"))), ggplot2::aes(x = variable)) +
  ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
  ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(by_income_source$`95%uci`)<2){
    2
  } else {
    max(by_income_source$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Mortality Rates")+
  ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) +
  ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))+
  ggplot2::facet_wrap(~group, ncol = 5)
```

```{r, fig.height=8,fig.width=7}
plot_results.summary_income_source
```

##### Birth

```{r, include=FALSE}
birth <- results_mort %>%
  dplyr::mutate(`point.est` = as.numeric(birth_rate),
                `95%lci` = as.numeric(stringr::str_extract(birth_rate_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(birth_rate_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "Birth")

overall_birth <- birth %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(overall_birth)
```

```{r, include=FALSE}
plot_results.summary.birth <- ggplot2::ggplot(overall_birth, ggplot2::aes(x = variable)) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(overall_birth$`95%uci`)<2){
    2
  } else {
    max(overall_birth$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Birth Rates")
```

```{r}
plot_results.summary.birth
```

##### Birth By Admin 1

```{r, include=FALSE}
birth_admin1 <- results_mort_admin1 %>%
  dplyr::mutate(`point.est` = as.numeric(birth_rate),
                `95%lci` = as.numeric(stringr::str_extract(birth_rate_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(birth_rate_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group,`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "Birth") %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(birth_admin1)
```

```{r, include=FALSE}
plot_results.summary.birth_admin1 <- ggplot2::ggplot(birth_admin1, ggplot2::aes(x = variable)) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(birth_admin1$`95%uci`)<2){
    2
  } else {
    max(birth_admin1$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Birth Rates")
```

```{r}
plot_results.summary.birth_admin1
```

##### Birth By Population Group

```{r, include=FALSE}
birth_pop_group <- results_mort_pop_group %>%
  dplyr::mutate(`point.est` = as.numeric(birth_rate),
                `95%lci` = as.numeric(stringr::str_extract(birth_rate_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(birth_rate_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(group,`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "Birth") %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(birth_pop_group)
```

```{r, include=FALSE}
plot_results.summary.birth_pop_group <- ggplot2::ggplot(birth_pop_group, ggplot2::aes(x = variable)) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(birth_pop_group$`95%uci`)<2){
    2
  } else {
    max(birth_pop_group$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Birth Rates")
```

```{r}
plot_results.summary.birth_pop_group
```


##### Cause of death by Admin1 

```{r, results='asis'}
cause_death_table_Admin1 <- srvyr.designs[[died_Sheet]] %>% 
  dplyr::group_by(!!rlang::sym(admin1),!!rlang::sym(death_cause)) %>% 
  dplyr::summarise(prop_cause = srvyr::survey_prop(vartype = "ci")) %>% 
  dplyr::mutate(!!rlang::sym(admin1) := get.choice.label(!!rlang::sym(admin1), get.choice.list.from.name(admin1)),
                !!rlang::sym(death_cause) := get.choice.label(!!rlang::sym(death_cause), get.choice.list.from.name(death_cause))) %>% 
  dplyr::mutate_at(vars(starts_with("prop_")),~ paste0(round(.*100,2),"%")) %>% 
  dplyr::rename_with(~stringr::str_remove(., "prop_"), starts_with("prop_"))

subch(DT::datatable(cause_death_table_Admin1, options = tableFormat))
```

##### Cause of death by population status

```{r, results='asis'}
cause_death_table_pop_status <- srvyr.designs[[died_Sheet]] %>% 
  dplyr::group_by(!!rlang::sym(population_group),!!rlang::sym(death_cause)) %>% 
  dplyr::summarise(prop_cause = srvyr::survey_prop(vartype = "ci")) %>% 
  dplyr::mutate(!!rlang::sym(death_cause) := get.choice.label(!!rlang::sym(death_cause), get.choice.list.from.name(death_cause))) %>% 
  dplyr::mutate_at(vars(starts_with("prop_")),~ paste0(round(.*100,2),"%")) %>% 
  dplyr::rename_with(~stringr::str_remove(., "prop_"), starts_with("prop_"))

subch(DT::datatable(cause_death_table_pop_status, options = tableFormat))
```

##### % of DEATHS that SOUGHT CARE in Previous 2 Weeks by Admin1

```{r, results='asis'}
died_healthcare_death_table_admin1 <- srvyr.designs[[died_Sheet]] %>% 
  dplyr::group_by(!!rlang::sym(admin1),!!rlang::sym(died_healthcare_yn)) %>% 
  dplyr::summarise(prop_seek_healthcare = srvyr::survey_prop(vartype = "ci")) %>% 
  dplyr::mutate(!!rlang::sym(admin1) := get.choice.label(!!rlang::sym(admin1), get.choice.list.from.name(admin1))) %>% 
  dplyr::filter(!!rlang::sym(died_healthcare_yn) == yes_seek_healthcare) %>% 
  dplyr::mutate_at(vars(starts_with("prop_")),~ paste0(round(.*100,2),"%")) %>% 
  dplyr::rename_with(~stringr::str_remove(., "prop_"), starts_with("prop_")) %>% 
  dplyr::select(-died_healthcare_yn)

subch(DT::datatable(died_healthcare_death_table_admin1, options = tableFormat))
```

##### % of DEATHS that SOUGHT CARE in Previous 2 Weeks by population status

```{r, results='asis'}
died_healthcare_death_table_pop_status <- srvyr.designs[[died_Sheet]] %>% 
  dplyr::group_by(!!rlang::sym(population_group),!!rlang::sym(died_healthcare_yn)) %>% 
  dplyr::summarise(prop_seek_healthcare = srvyr::survey_prop(vartype = "ci")) %>% 
  dplyr::filter(!!rlang::sym(died_healthcare_yn) == yes_seek_healthcare) %>% 
  dplyr::mutate_at(vars(starts_with("prop_")),~ paste0(round(.*100,2),"%")) %>% 
  dplyr::rename_with(~stringr::str_remove(., "prop_"), starts_with("prop_")) %>% 
  dplyr::select(-died_healthcare_yn)

subch(DT::datatable(died_healthcare_death_table_pop_status, options = tableFormat))
```


```{r message=TRUE, warning=FALSE, include=FALSE}
## output XLSX files
file.list <- list.files(path = params['combine_folder'], pattern = "*.xlsx")
if(length(file.list) >0){
  file.list <- setNames(file.list, paste0(params['combine_folder'], file.list))
  df <- lapply(names(file.list), readxl::read_excel)
  names(df) <- stringr::str_remove(file.list, ".xlsx")
  sorted_df <- df
} else {
  sorted_df <- NULL
}


save.dfs.mortality(sorted_df, tables = c("overall",
                                         "by_gender",
                                         "by_age_group",
                                         "by_pop_group",
                                         "by_admin1",
                                         "by_admin2",
                                         "by_admin1_pop_group",
                                         "by_hoh_gender",
                                         "by_income_source",
                                         "overall_birth"),
                   paste0("output/Mortality_combined_analysis_toc_", strings['out_date'], ".xlsx"), use_template = F)

for (i in 1:length(names(sorted_df))){
  if (nchar(names(sorted_df)[i]) > 31){
    names(sorted_df)[i] <- stringr::str_trunc(names(sorted_df)[i], 28)
    names(sorted_df)[i] <- paste0(names(sorted_df)[i],i)
  } else{
    names(sorted_df) <- names(sorted_df)
  }
}
by_overall <- overall %>% 
  dplyr::filter(variable == "cmr") %>% 
  dplyr::mutate(admin1 = "national") %>% 
  dplyr::select(admin1, point.est,`95%lci`,`95%uci`)
## admin1 for MSNA Integrated Analysis Tables
table_by_admin1 <- by_admin1 %>% 
  dplyr::filter(variable == "cmr") %>% 
  dplyr::select(admin1,point.est,`95%lci`,`95%uci`) 

table_by_admin1 <- rbind(table_by_admin1,by_overall)

openxlsx::write.xlsx(table_by_admin1, file = paste0("./output/MSNA_Integrated_Table", strings['out_date'], ".xlsx"))
```

