---
title: "Mortality Descriptive Analysis Report"
subtitle: "`r Sys.Date()`"
output: html_document
---

<style>
.tocify-subheader {
  font-size: 0.7em;
}
.tocify-item {
  font-size: 0.85em;
  padding-left: 25px;
  text-indent: 0;
}
</style>


```{r logo, echo=FALSE}
htmltools::img(src = knitr::image_uri("resources/Logo_Reach_RGB_1.png"),
               alt = "REACH logo",
               style = 'position:absolute; top:0; right:0; padding:0; margin:20; width:250px')
```



```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
  options(scipen = 999)
  rm(list=ls()[!ls() %in% c("params", "strings", "language")])
  
  source("src/init.R")

  ##############################################################################################################

  ## FIX A FEW THINGS TO ALIGN DATA & TOOL WITH ANALYSIS SCRIPT
  
  source("src/fix_bugged_names.R")
  
  ## ADDING WEIGHTS, OVERALL AND GROUPING VARIABLES 

  source("src/format_dataset.R")  # <- additional indicators and grouping variables are added here 
  

  # all additional columns from data that need to be included in srvyr designs (need to be present in all sheets):
  special_vars <- c("overall", "weight", daf$admin) %>% unique  

```

```{r setup2, include=FALSE}

  ## FINAL TOUCHUPS TO DAF, CONVERTING COLUMNS
  ################################################################################
  
  ## a lookup tibble for variable/column names:
  var_lookup <- tibble()
  for (sheet in names(data.list)){
    var_lookup <- rbind(var_lookup, tibble(variable = names(data.list[[sheet]]), datasheet = sheet)) %>% 
      distinct(variable, .keep_all = T) %>% filter(stringr::str_detect(variable, "(/)|(___)", T))
                                                       # ^ here, I am assuming that no one will put a variable in the DAF that contains '/' or '___', or starts with '_'
        # also note that by using distinct here, if the same variable appears in multiple sheets, then by default the first sheet will be used (so: main usually)
  }
 # ADD DATASHEET COLUMN TO DAF
  if(!"datasheet" %in% names(daf)) daf <- daf %>% left_join(var_lookup, by = "variable")
  
  missing_sheets <- daf %>% filter(is.na(datasheet)) %>% pull(variable)
  if(length(missing_sheets) > 0) stop("These variables are missing from data: ", paste(missing_sheets))
  rm(missing_sheets)

 # CONVERT!
  source("src/convert_cols_with_daf.R")


  ## SRVYR DESIGNS
  ##############################################################################

  srvyr.designs  <- list()
  
  for(sheet in names(data.list)){
    daf_vars <- daf %>% filter(var_type != "select_multiple" & datasheet == sheet) %>% pull(variable)
  
    daf_vars_sm <- daf %>% filter(var_type == "select_multiple" & datasheet == sheet) %>% pull(variable)
    sm_vars_pattern <- paste0("^",paste0("(",daf_vars_sm,")", collapse = "|"))
    
    daf_disaggs <- daf %>% filter(!isna(disaggregations) & datasheet == sheet) %>% pull(disaggregations) %>% stringr::str_split(" *; *") %>% unlist %>% unique
    daf_disaggs <- daf_disaggs[daf_disaggs!=""]
    
    survey_data <- data.list[[sheet]] %>% select(all_of(special_vars), all_of(daf_vars), all_of(daf_disaggs), matches(sm_vars_pattern))
    
    srvyr.designs[[sheet]] <- srvyr::as_survey_design(survey_data, weights = NULL)
    
    rm(survey_data, daf_vars, daf_vars_sm, daf_disaggs)
  }

  
```

# {.tabset .tabset-fade}

## Introduction

```{r, results='asis'}
cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What is this tool?"))
cat('\nThe Mortality Descriptive Analysis is an analytical platform that presents a multitude of quantitative data tables. It encompasses a wide range of Mortality indicators collected through the assessment process, empowering users to examine and interpret complex datasets effectively. This tool is structured to support understanding the distribution of your data and support you writing your factsheets/outputs/reports, and create other visualizations.')
cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What is in this tool?"))
cat('\nWithin this tool, users will find a wealth of information organized into distinct categories, each pertaining to critical aspects of humanitarian analysis:')
cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",4), collapse=""), " ", "Mortality"))
cat('\nExplore data on Mortality.')
cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "What else to know?"))
cat('\nAs you saw in the output folder, you will have another excel file outputed from the analysis script. The Excel file includes 2 sheets. The first 2 are all the tables that you see in the different sections of this HTML output. You can navigate to respective tables through the first sheet "Table of Contents".')
cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",3), collapse=""), " ", "Feedback"))
cat('\nFeedback on improvements to this product can be done through reaching out to:\n\n-abraham.azar@impact-initiatives.org \n\n -impact.geneva.phu@impact-initiatives.org')
```


```{r, results='asis'}
sections <- daf %>% select(section) %>% distinct() %>% pull()

# produce HTML output: go line by line of the analysis flan and generate each section or table

for (i in sections){
  add_to_html.section(i)
  daf.section <- daf %>% filter(section == i)
  
  progress.bar.title <- as.character(Sys.time())
  pb <- tcltk::tkProgressBar(progress.bar.title, paste0("[", i, "] Number of entries executed"), 0, nrow(daf.section), 0, width = 500)
  
  for (r in 1:nrow(daf.section)){
    tcltk::setTkProgressBar(pb, r, progress.bar.title, paste0("[", i, "] Number of entries executed: ", r, " of ", nrow(daf.section)))
    
    # read entry from analysis flan
    entry <- load_entry(daf.section[r,])
    
    add_to_html.title(entry$label)
    cat(paste0("\n\nVariable name: <em><strong>", entry$variable),"</strong></em>")
    cat(entry$comments)
    
    # get the appropriate data source:
    srvyr.design <- srvyr.designs[[entry$datasheet]]
    
    # filter out NAs
    if(entry$omit_na) srvyr.design <- srvyr.design %>% filter(!is.na(!!sym(entry$variable)))
    
    # check if any data for this variable is left at all
    if(nrow(srvyr.design) == 0) {
      cat("\n\nNo data for this variable (all NA).\n")
      next
    }else{
      if(!entry$omit_na){
        cat(paste("\n\nIncluding NA values.\n"))
      }else{
        cat(paste("&emsp;|&emsp;",as_perc((nrow(srvyr.design))/nrow(data.list[[entry$datasheet]])),"of respondents answered this question.\n"))
      }
    }
    
    # group by admin:
    srvyr.design <- srvyr.design %>% group_by(!!sym(entry$admin))
    
    # loop through each disagg.var
    for (disagg.var in entry$disaggregate.variables) {
      if(!isna(disagg.var)) cat("\nDisaggregated by:<em><strong>", paste0(disagg.var),"</strong></em>")
      if(!is.na(disagg.var)){
        res <- make_table(srvyr.design, entry, disagg.var) %>% ungroup %>% select(-any_of("overall")) %>%
          filter(!is.na(disagg.var))
      } else {
        res <- make_table(srvyr.design, entry, disagg.var) %>% ungroup %>% select(-any_of("overall")) 
      }

      # add overall
      if(entry$admin != "overall"){
        entry.ovrl <- entry
        entry.ovrl$admin <- "overall"
        if(!"overall" %in% (srvyr.design %>% variable.names)) srvyr.design <- srvyr.design %>% mutate(overall = "overall")
        res.overall <- make_table(srvyr.design %>% ungroup %>% group_by(overall),
                                        entry.ovrl, disagg.var)  %>% 
          mutate(!!sym(entry$admin) := "overall") %>% 
          ungroup %>% select(-any_of("overall"))
        res <- res %>% bind_rows(res.overall) %>% distinct
      }
      # save the xlsx
      xlsx_name <- paste0(entry$xlsx_name, ifelse(isna(disagg.var), "", paste0("_by_", disagg.var)))
      writexl::write_xlsx(res, paste0(params["combine_folder"],"/",xlsx_name,".xlsx"))
    
      subch(DT::datatable(res, options = tableFormat))
    }
    
  }
  close(pb)
}

```

```{r message=TRUE, warning=FALSE, include=FALSE}
## output XLSX files
file.list <- list.files(path = params['combine_folder'], pattern = "*.xlsx")
file.list <- setNames(file.list, paste0(params['combine_folder'], file.list))
df <- lapply(names(file.list), readxl::read_excel)
names(df) <- stringr::str_remove(file.list, ".xlsx")

sorted_df <- df

save.dfs(sorted_df,paste0("output/FSL_combined_analysis_toc_", strings['out_date'], ".xlsx"), use_template = F)

for (i in 1:length(names(sorted_df))){
  if (nchar(names(sorted_df)[i]) > 31){
    names(sorted_df)[i] <- stringr::str_trunc(names(sorted_df)[i], 28)
    names(sorted_df)[i] <- paste0(names(sorted_df)[i],i)
  } else{
    names(sorted_df) <- names(sorted_df)
  }
}

```

## Mortality [Part 2] {.tabset .tabset-fade}

### Demographics {.tabset .tabset-fade}

#### Age pyramid in years disaggregated by gender 

```{r, message=FALSE}
impactR4PHU::plot_age_pyramid(df_mortality_long %>% 
                                  filter(is.na(left),
                                         is.na(death)))
```

#### Age pyramid in years disaggregated by gender per Team

```{r, results='asis', echo=FALSE}
if(yes_no_team == "yes"){
    list_teams <- raw.main[[team]] %>% unique()
    for (i in list_teams) {
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong> {.tabset .tabset-fade}"))
      list_enum <- raw.main %>% 
        dplyr::filter(!!rlang::sym(team) %in% i) %>% 
        dplyr::pull(!!rlang::sym(enumerator))%>% 
        unique()
      for (j in list_enum){
        cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",6), collapse=""), " ", "<strong>",j,"</strong>"))
        subch(impactR4PHU::plot_age_pyramid(df_mortality_long %>% 
                                              dplyr::filter(is.na(left),
                                                            is.na(death),
                                                            !!rlang::sym("enumerator") %in% j)),
            fig_height = 5, fig_width = 7)
      }
    }
} else {
    list_enum <- df_mortality_long[["enumerator"]]%>% unique
    for (i in list_enum) {
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>Enumerator: ",i,"</strong>"))
      subch(impactR4PHU::plot_age_pyramid(df_mortality_long %>% 
                                      dplyr::filter(is.na(left),
                                             is.na(death),
                                             !!rlang::sym("enumerator") %in% i)),
            fig_height = 5, fig_width = 7)
    }
  }

```

#### Histogram of age in years

```{r, message=FALSE}

  impactR4PHU::plot_age_distribution(df_mortality_long %>%
                                       filter(is.na(left),
                                              is.na(death)),
                                     year_or_month = "year",
                                     max_age = 10)

```

#### Histogram of age in years per Team

```{r, results='asis', message=FALSE}
if(yes_no_team == "yes"){
    list_teams <- raw.main[[team]] %>% unique()
    for (i in list_teams) {
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong> {.tabset .tabset-fade}"))
      list_enum <- raw.main %>% 
        dplyr::filter(!!rlang::sym(team) %in% i) %>% 
        dplyr::pull(!!rlang::sym(enumerator))%>% 
        unique()
       for (j in list_enum){
          cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",6), collapse=""), " ", "<strong>",j,"</strong>"))
          subch(impactR4PHU::plot_age_distribution(df_mortality_long %>%
                                               filter(is.na(left),
                                                      is.na(death),
                                                      !!rlang::sym("enumerator") %in% j),
                                             year_or_month = "year",
                                             max_age = 10,
                                             by_group = "enumerator"),
                fig_height = 8)
       }
    }
} else {
    subch(impactR4PHU::plot_age_distribution(df_mortality_long %>%
                                       filter(is.na(left),
                                              is.na(death)),
                                     year_or_month = "year",
                                     max_age = 10,
                                     by_group = "enumerator"),
                fig_height = 8)
  }
```

#### Histogram of age in months

```{r, fig.width = 10, warning=FALSE, message=FALSE}
  impactR4PHU::plot_age_distribution(raw.hh_roster,
                                     year_or_month = "month",
                                     age_months = age_roster_month,
                                     breaks = 1)

```

#### Histogram of age in months per Team

```{r, results='asis',  warning=FALSE}
if(yes_no_team == "yes"){
    for (i in list_teams) {
      cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",5), collapse=""), " ", "<strong>",i,"</strong> {.tabset .tabset-fade}"))
      plot_raw.main <- raw.main %>%
        dplyr::rename(uuid = uuid_main) %>%
        dplyr::filter(!!rlang::sym(team) == i)

      plot_raw.hh_roster <- raw.hh_roster %>%
        dplyr::rename(uuid = uuid_roster) %>%
        dplyr::filter(uuid %in% plot_raw.main$uuid)
      list_enum <- raw.main %>% 
        dplyr::filter(!!rlang::sym(team) %in% i) %>% 
        dplyr::pull(!!rlang::sym(enumerator))%>% 
        unique()
      for (j in list_enum){
        cat(paste0(paste0(rep("\n",2), collapse=""), paste0(rep("#",6), collapse=""), " ", "<strong>",j,"</strong>"))
        subch(impactR4PHU::plot_age_distribution(plot_raw.hh_roster %>%
                                             dplyr::left_join(select(plot_raw.main, c("uuid", enumerator))) %>%
                                             dplyr::filter(!!rlang::sym(enumerator) == j),
                                           year_or_month = "month",
                                           age_months = age_roster_month,
                                           by_group = enumerator,
                                           breaks = 1),
              fig_height = 8, fig_width = 10)
      }
    }
} else {
  plot_raw.hh_roster <- raw.hh_roster %>%
    dplyr::rename(uuid = uuid_roster)
  plot_raw.main <- raw.main %>%
    dplyr::rename(uuid = uuid_main)

  subch(impactR4PHU::plot_age_distribution(plot_raw.hh_roster %>%
                                       dplyr::left_join(select(plot_raw.main, c("uuid", enumerator))),
                                     year_or_month = "month",
                                     by_group = enumerator,
                                     age_months = age_roster_month,
                                     breaks = 1),
              fig_height = 8, fig_width = 10)
}
```

### Results

#### Number of Death/Joiners/Leavers & Person Time per Enumerator

```{r, include=FALSE}
table_djl_enum <- df_mortality_long %>%
  dplyr::group_by(enumerator) %>%
  dplyr::summarise(Leavers = sum(as.numeric(left), na.rm = T),
                   Joiners = sum(as.numeric(join), na.rm = T),
                   Death = sum(as.numeric(death), na.rm = T),
                   `Death Under 5` = sum(as.numeric(death_under5), na.rm = T),
                   `Person Time` = sum(as.numeric(person_time), na.rm = T),
                   `Person Time Under 5` = sum(as.numeric(under_5_pt), na.rm = T))

total <- table_djl_enum %>%
  dplyr::group_by() %>%
  dplyr::summarise(Leavers = sum(as.numeric(Leavers), na.rm = T),
                   Joiners = sum(as.numeric(Joiners), na.rm = T),
                   Death = sum(as.numeric(Death), na.rm = T),
                   `Death Under 5` = sum(as.numeric(`Death Under 5`), na.rm = T),
                   `Person Time` = sum(as.numeric(`Person Time`), na.rm = T),
                   `Person Time Under 5` = sum(as.numeric(`Person Time Under 5`), na.rm = T)) %>%
  dplyr::mutate(enumerator = "Total") %>%
  dplyr::relocate(enumerator, .before = 1)

table_djl_enum <- bind_rows(table_djl_enum, total)
```

```{r, results='asis'}
DT::datatable(table_djl_enum)
```

#### Mortality Rates

```{r, include=FALSE}
crude <- results_mort %>%
  dplyr::mutate(`point.est` = as.numeric(cdr),
                `95%lci` = as.numeric(stringr::str_extract(cdr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(cdr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "cmr")

under5 <- results_mort %>%
  dplyr::mutate(`point.est` = as.numeric(u5dr),
                `95%lci` = as.numeric(stringr::str_extract(u5dr_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(u5dr_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "u5mr")

results.summary <- rbind(crude,under5) %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(results.summary)
```

```{r, include=FALSE}
plot_results.summary <- ggplot2::ggplot(results.summary %>%
                                               mutate(variable = case_when(variable == "cmr"~"Crude",
                                                                           variable == "u5mr"~"Under 5")), ggplot2::aes(x = variable)) +
  ggplot2::geom_hline(yintercept=1, linetype='dotted', color = 'black', size =1)+
  ggplot2::geom_hline(yintercept=2, linetype='dotted', color = 'red', size =1)+
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, if(max(results.summary$`95%uci`)<2){
    2
  } else {
    max(results.summary$`95%uci`)
  }))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Mortality Rates")+
  ggplot2::labs(caption = c("Black Dotted Line: Crude Threshold (WHO)", "Red Dotted Line: Under 5 Threshold (WHO)")) +
  ggplot2::theme(plot.caption = ggplot2::element_text(hjust = c(0.2,0.8),color = c("black","red")))
```

```{r}
plot_results.summary
```

#### Birth Rates

```{r, include=FALSE}
birth <- results_mort %>%
  dplyr::mutate(`point.est` = as.numeric(birth_rate),
                `95%lci` = as.numeric(stringr::str_extract(birth_rate_ci,"(?<=\\[)[^\\s\\-]*")),
                `95%uci` = as.numeric(stringr::str_remove(stringr::str_extract(birth_rate_ci,"(?<=-)[^\\]]*")," "))) %>%
  dplyr::select(`point.est`,`95%lci`,`95%uci`) %>%
  dplyr::mutate(variable = "Birth")

results.summary.birth <- birth %>%
  dplyr::relocate(variable, .before = 1)
```

```{r, results='asis'}
DT::datatable(results.summary.birth)
```

```{r, include=FALSE}
plot_results.summary.birth <- ggplot2::ggplot(results.summary.birth, ggplot2::aes(x = variable)) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin =`95%lci`, ymax = `95%uci`, width = 0.2, color = "red"))+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%lci`, label = `95%lci`, vjust = 1.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = `95%uci`, label = `95%uci`, vjust = -0.5, color = "red", fontface = "bold"), size = 3)+
  ggplot2::geom_point(ggplot2::aes(y = point.est), color = "blue")+
  ggplot2::geom_text(ggplot2::aes(x = variable, y = point.est, label = point.est, hjust = -0.5), size = 3, color = "blue", fontface = "bold")+
  ggplot2::scale_y_continuous(limits=c(0, max(results.summary.birth$`95%uci`)))+
  ggplot2::theme(legend.position = "none", axis.title.y = ggplot2::element_blank())+
  ggplot2::xlab("Overall Birth Rates")
```

```{r}
plot_results.summary.birth
```


